### 2018-08-24 case_for_support.tex
First commit

\documentclass[11pt]{article}
  \usepackage[a4paper,bindingoffset=0cm,%
              left=2cm,right=2cm,top=2cm,bottom=2cm,%
              footskip=0.5cm]{geometry}
  \usepackage[pdftex]{graphicx}
  \usepackage{multicol}
  \usepackage{enumitem}
  %\usepackage{psfig}

  \usepackage{siunitx,amsmath,amssymb}

  \usepackage{sectsty}
  \sectionfont{\fontsize{12}{15}\selectfont}
  \subsectionfont{\fontsize{11}{15}\selectfont}

  %\renewcommand*\sfdefault{phv}
  %\renewcommand{\familydefault}{\sfdefault}
  \makeatletter
  \newenvironment{tablehere}
    {\def\@captype{table}}
    {}

  \newenvironment{figurehere}
    {\def\@captype{figure}}
    {}
  \makeatother

  \begin{document}
  %\title{Broadening the impact of astronomical data handling\vspace{-2ex}}
  %\maketitle
  \setcounter{figure}{0}
  \noindent
  {\LARGE \bf From Stars to Baht: Broadening the economic impact of \\
  astronomical data handling techniques in Thailand}

  \vspace{3mm}
  \noindent
  {\LARGE \bf Case for support}
  \vspace{3mm}

  \noindent
  We request funds to extend our previous GCRF-funded project

  research how the data archiving and analysis techniques we have developed as part of our previous STFC/Newton-funded project can be best adapted to address the needs of Thai businesses and organisations. To achieve this research aim, our multi-disciplinary team of Thai and UK scientists will spend 12 months working closely with a group of five pre-identified businesses and organisations based in Northern Thailand that have specific data archiving and analysis needs.

  \vspace{3mm}
  \noindent
  {\large \bf 1.1 Background: Using astronomy data to train Thai data scientists}

  \noindent
  As outlined in our ODA statement, there is strong evidence that improving access to advanced data handling and analysis techniques is one of the most effective ways of increasing productivity in businesses and organisations. This is most sustainable when using home-grown talent to provide these services. As such, providing relevant, high quality training in these digital skills to Thai students and workers is a major element in helping the Thai economy to graduate from middle to upper income.

  Facilitated by STFC funding via the Newton and GCRF programs our team of educators and researchers are developing a highly effective data science training programme for Thai students. As part of this programme, students work with external industries and organisations to gain first-hand experience in using data science to solve real-world problems. The first students involved in our training programme developed novel machine learning-based technologies to identify rare true positive sources within astronomy datasets which contained a much larger (i.e., by a factor of $>1000$) samples of false positives; an example of a heavily imbalanced dataset that off-the-shelf machine learning algorithms struggle to deal with.

  events within astronomy

  As a consequence of STFC funding (via the GCRF and Newton programs) our team of educators and researchers have been

  Since February, 2017, our team of educators and researchers from multiple disciplines and institutions have been

  However, Thai data scientists and their students typically lack access to very large amounts of digital data, restricting their training in ``Big Data'' science that is so crucial for the development of modern economies. To address this problem, we successfully applied for Newton funding (12-month project starting February, 2017) to give the Thai data scientists in our team research experience of working with large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO). GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}. This large, constantly-updated dataset has given our research team the opportunity to develop the skills and techniques needed to handle and analyse the kinds of Big Data generated by many of today's industries.

  \vspace{2mm}
  \noindent
  The primary {\it research} goals of our Newton project were to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated Machine-Learning (ML) algorithms capable of quickly and robustly categorising sources detected by GOTO. Our research has led to some novel solutions. For the database component we are developing a hybrid system that combines the structure of a relational database (such at that used by SDSS) with the flexibility of a non-relational database (which are popular within tech. industries). For the ML component, we are developing a new two-stage categorisation algorithm which uses unsupervised ML algorithms to quickly remove obvious artefacts from our data before passing more ambiguous cases to a supervised ML algorithm. Since both goals are to address challenges associated with archiving and analysing large amounts of astronomical data, the science, technology and expertise involved in the proposed GCRF project has originated from work associated with STFC's core Science Programme.

  \vspace{3mm}
  \noindent
  {\large \bf 1.2 Broadening the impact of our research to local businesses and organisations}

  \noindent
  At present, the impact of our Newton project is limited to the people directly involved in the project (i.e., Thai and UK astronomers, Thai data scientists and their students), whereas our long-term ambition has always been to broaden the impact of our research to develop the wider Thai economy. In this regard the goal of this GCRF project is to use the technology and skills we have developed to increase the productivity of Thai businesses and organisations. To do this effectively, our team needs to first gain experience of working with such external parties to research how best to adapt our technologies and expertise to their data handling and analysis needs.

  \vspace{2mm}
  \noindent
  For this partnership-building project, we request funds to research how our data archiving and analysis techniques can be adapted to meet the needs of five pre-identified Thai businesses and organisations (hereafter, ``external partners''; see Table 1). All our external partners are based in areas local to the Thai co-Is and have already agreed to work with us throughout the 12-month project (see Letters of Support). At this ``capacity building'' stage, we prefer to limit the number of external partners as it ensures that all parties have a thorough understanding of the goals and expectations of the project from the outset. In addition to our research goals, our aim is to learn lessons and define commonalities of approach that can be applied when we expand the project to work with larger numbers of external partners. Our ambition is to apply for follow-on GCRF funding to support this expansion.

  \begin{table}[h]
  \begin{tabular}{p{2.8cm}|p{13.4cm}}
    {\it Partner} & {\it Data handling/analysis needs}\\
    \hline
    \hline
      Thanapiriya plc & A food retail business that wishes to take multiple factors into account to predict optimum stock volumes. This is a categorisation problem (the same type faced with GOTO data) in terms of increase/decrease/no-change of product demand.\\
    \hline
      TAPP Auto & A car sales business seeking to develop a system that can predict the depreciation curve of a given vehicle given multiple input factors. This is a regression and ``missing data'' problem, as commonly found in astronomy data analysis.\\
    \hline
       Pibulsongkram Raj. University & The Academic Resources Office wishes to identify the optimum online resources to meet the needs of different types of users. This can be achieved through ML-based Personalised Service Provision as often used by streaming services.\\
    \hline
      MFU & The Student Office seeks a system to identify the causes of the high student dropout rates in Thai Universities. This is, in part, a categorisation problem, since students can be grouped according to different drop-out factors. \\
    \hline
      M-Store & A retail complex based on MFU's campus seeks to increase footfall by targeting promotions to specific groups. A ML-based clustering analysis will help to identify different categories according to customer information. \\
    \hline
  \end{tabular}
  \caption{\it Our external partners and a brief description of their data handling and analysis needs. }
  \vspace{-5mm}
  \end{table}
  \vspace{3mm}
  \noindent
  {\large \bf 1.3 Description of work to be undertaken}

  \noindent
  Over the twelve month period of the grant, we will (in broadly chronological order; see Gantt Chart):
  \begin{enumerate}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
  \item Have the Thai staff and students currently working on the project visit the UK. The purpose of this visit is provide the students with first-hand experience of presenting to and communicating with their first external partner -- the GOTO collaboration.
  \item Host a networking event in Chiang-Rai, Thailand, where most of the Thai co-Is and external partners are based. All team members and representatives from all external partners will attend. At the event, our team will deliver a series of short presentations to highlight our skills and technology, using GOTO as a case study. Representatives from our external partners will describe their businesses/organisations, the data they hold, and agree with the team their desired outcomes from the project, together with an estimate of their impact.
  \item Each external partner will be assigned at least one primary team member contact (this could be a postgraduate student, in which case a staff researcher will act as a secondary contact). The primary contact will attend on-site fortnightly meetings with the external partner to get to fully understand their data and analysis needs. Such close interaction is vital in order to discriminate between informative vs. non-informative data. After each meeting, the primary contact will report back to the rest of the team to ensure a collaborative effort is maintained. Start researching and testing possible solutions to the external partners' needs.
  \item We will host a second networking event in month 5. By this stage, the team will have a thorough understanding of the data and needs of each external partner and will have researched possible solutions, enabling us to decide on the broad design of what we will deliver to each partner. This design will be discussed and agreed-upon by the external partners during the networking event. 
  \item Our work will focus on delivering the agreed systems by adapting our own and further researching new techniques to meet our partners' needs. As this happens, the purpose of the fortnightly meetings will progressively shift toward feedback sessions, during which the primary contact will demonstrate our systems and allow the end user to suggest improvements. 
  \item At the start of month ten, we will deliver ``Beta versions'' of the systems we have developed. We will train the external partners on how to use the systems and collect any immediate feedback they may have. The systems will then go through a two month-long Beta testing phase by the external partners, who will then report their experience back to the team. During months eleven and twelve we will address any feedback from the Beta testing phase to deliver the final product.
  \item We will host a final networking event to discuss the outcomes, successes/drawbacks, impact-to-date, and future directions of the research and partnerships. This event will coincide with an outreach event to highlight to the public and invited representatives from other businesses/organisations the economic benefits of data science. Part of the goal of this event is to identify future partnerships.
  \end{enumerate}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace{3mm}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \noindent
  {\large \bf 1.4 Maximising the impact of the project}

  \noindent
  The steps we have taken to ensure that the project has maximal impact are described fully in our Pathways to Impact statement. Briefly, our choice of working very closely with a limited number of external partners is motivated by our desire to focus our efforts to ensure maximal impact in terms of our partners' productivity {\it and} building our team's capacity for working with external partners. This experience will establish protocols and ways of working to be taken forward to future partnerships.

  \vspace{2mm}
  \noindent
  In addition to the impact within Thailand, the project promises secondary benefits to UK research. With STFC's involvement in forthcoming data-intensive projects such as the LSST and SKA, it is vitally important that UK astronomers gain exposure to advanced data handling and analysis techniques. Further, the proposed work will give the team experience of working with data-intensive businesses -- valuable preparation for research supported by the UK Government's Industrial Strategy.

  \vspace{3mm}
  \noindent
  {\large \bf 2.1 Management plan}

  \noindent
  The success of each external partnership will be a team effort. During and following the first networking event we will set out a series of milestones to reach in order to achieve each partner's desired outcome. After consulting with the rest of the team, Drs. Boongoen and Mullaney will assign primary contacts by matching team members' skills and experience to the needs of the external partners. Dr. Boongoen will coordinate the fortnightly partner meetings. At the end of each of their fortnightly meetings, the primary contact will write a brief meeting summary which will be discussed with, agreed, and signed-off by the external partner. These summaries will be collated and shared among the whole team prior to our fortnightly team meetings/telecons. During our minuted team meetings/telecons we will decide what short term actions should be taken, and by whom, to reach the intermediate milestones and the desired goals of the external partners, and whether any of these need to be reassessed with the partners. By pooling our resources and focussing on a limited number of external partners we mitigate the risk that the needs of any one partner will go unmet. Finalising, during the second networking event, a broad design of what will be delivered for Beta testing avoids the risk of not delivering a coherent system for Beta testing. The design can still evolve after this stage, but this approach ensures any evolution will be managed. There is the risk that an external partner may be unsatisfied with the proposed design of the Beta system. If that happens, it will be the responsibility of Drs. Boongoen and Mullaney (as PIs) to negotiate a solution. Should a viable solution not be found, it is feasible that a partner may leave the collaboration. This risk to the project is mitigated by having multiple partners, while the team would still have learned valuable lessons from the experience to carry-over into future partnerships.

  \vspace{3mm}
  \noindent
  {\large \bf 2.2 Track record of applicants}

  \noindent
  Our multi-disciplinary team of researchers is made up of astronomers, computer and data scientists, a computer hardware specialist, and a Lecturer in Business Management and Marketing. The UK PI (Mullaney) is an astronomer with extensive experience of analysing data from large astronomical surveys. He was the UK PI of our Newton-funded project, responsible for ensuring that the research meets the needs of the GOTO collaboration. The Thai PI (Boongoen) is a computer scientist with specialist expertise in developing ML algorithms. He has extensive experience in managing research projects, having PI'd four successful grants in the last four years. Dr. Iam-on is data scientist with expertise in database design, data mining, and developing ML algorithms for automated data analysis. She will oversee the database design elements of the project as well as contributing her expertise on the automated analysis aspect. Dr. Eungwanichayapant's background is in high energy astrophysics, with particular expertise in developing unsupervised ML algorithms to analyse data from Gamma Ray telescopes. Drs. Sawangwit and Awiphan are astronomers based in Thailand. Their research expertise lies in analysing large astronomical datasets and time varying data, and thus are very relevant to the project. Mr. Vattayasak will be the team's computer hardware expert: his specialism is in setting up distributed networks of computers to host large, distributed databases. Finally, Ms. Noichankgkid is a Lecturer in Business Management and Marketing, with extensive management and finance experience prior to and during her academic career. Her experience will prove invaluable when liaising with and establishing the needs of our business partners.

  \end{document}

  %\noindent
  %The aim of this project is to research how to adapt and build-upon the databasing and machine-learning technologies we have developed to best satisfy the data handling/analysis needs of our five external partners. Our goal is that this research will increase our partners' productivity, which will first be assessed qualitatively via partner feedback then, after 12 months, quantitatively through data analysis. The project is the next step in our long-term ambition to establish a self-sustaining ``Centre of Excellence'' that will deliver data solutions to a wide range of businesses and organisations in northern Thailand.

### 2018-08-24 data_management.tex
First commit

\documentclass[11pt]{article}
\usepackage[a4paper,bindingoffset=0cm,%
            left=2cm,right=2cm,top=2cm,bottom=2cm,%
            footskip=0.5cm]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{multicol}

%\usepackage{psfig}

\usepackage{siunitx,amsmath,amssymb}

\usepackage{sectsty}
\sectionfont{\fontsize{12}{15}\selectfont}
\subsectionfont{\fontsize{11}{15}\selectfont}

%\renewcommand*\sfdefault{phv}
%\renewcommand{\familydefault}{\sfdefault}
\makeatletter
\newenvironment{tablehere}
  {\def\@captype{table}}
  {}

\newenvironment{figurehere}
  {\def\@captype{figure}}
  {}
\makeatother

\begin{document}
%\title{Broadening the impact of astronomical data handling\vspace{-2ex}}
%\maketitle
\setcounter{figure}{0}
\noindent
{\LARGE \bf From Stars to Baht: Broadening the economic impact of \\
astronomical data handling techniques in Thailand}

\vspace{3mm}
\noindent
{\LARGE \bf Data management plan}

\vspace{3mm}
\noindent
We will ensure from the outset that protocols are in place to systematically manage all data associated with the project. By the nature of the research, the project will collect and produce diverse datasets. The raw data we will receive from our external partners will be in the form of digital values and strings in either ascii (.csv) or excel spreadsheets. One of the aims of this project is to make this data more searchable and accessible for our external partners by setting up relational and/or non-relational databases to contain this data. The data derived from our ML analysis can be stored more simply, in ascii files, for example.

\vspace{2mm}
\noindent
Because of their potentially commercially sensitive nature, any data transferred between the external partners and our team will be done so in an encrypted state (whether by physical media such as USB stick or over the internet). Once on site at MFU, the raw data will immediately be backed-up on MFU's multiple backup servers. Once this has been done, raw data will be sent (via ssh, which is encrypted once the connection is established) to the UK to be backed up on Sheffield's secure servers. A Structured Query Language (SQL) database will be created to track all digital files.

\vspace{2mm}
\noindent
Once the original raw data are backed-up on both sites, work will start on researching the best means to incorporate the data into a distributed non-relational database. The data management system we will use for this is {\it Hadoop}, which is widely used throughout the IT sector, thus ensuring the long-term readability of the data. Most of our data analysis will take place within the {\it Orange} data mining software environment, which is an open-source and under constant development. These steps ensure that the data collected and produced by the project will be readable for at least 10 years.

\vspace{2mm}
\noindent
The main data that will be of use to other researchers are descriptions of the technologies we will develop to address the needs of the external partners. As with any research, our project will involve trial and error - testing different databasing and analysis techniques. The main publishable outcome of the work will be the results from these tests in terms of accuracy, reliability and speed of the database system and the ML-based analysis. By signing the Letter of Support, our external partners already have an understanding of this. Where not commercially sensitive, all raw data will be made publicly available, together with any non-commercially sensitive derived data. This includes data from Pibulsongkram Rajabhat University (User behaviour and service provision) and MFU (Academic and educational development office and M-Store).

\vspace{2mm}
\noindent
 The outcome of our research  -- the completed database design and working model -- will be made available by enacting the Release to Public policies of Mae Fah Luang University. We will package our data analysis algorithms in an {\it Orange} module as well as providing a self-contained software package complete with user interface to the external partner. Any non-commercially sensitive code will be shared publicly using the GitHub software sharing website.

% to protect our research findings, and publicly available Internet resources to share our results.  All aspects of the research will be carefully tracked, stored, and published.  The work detailed in the preceding proposal can be anticipated to produce three broad categories of data:  computer software, user-specific data, and models. The computer software category includes not only the Hadoop ecosystem, but also the Orange –Data mining tool (open source). The data category includes data collections and associated meta-data specific to different pre-identified users. An officially signed agreement on data protection between the research team and each of the users is to be implemented. The model category includes the development of frameworks and algorithms, which will be logged through both handwritten research notebooks as well as digitally generated documents.

% \vspace{2mm}
% \noindent
% To ensure the safety of the data, we will use the School of Information Technology’s existing file server to periodically backup the materials.  A Structured Query Language (SQL) database will be created to track the digital documents. The completed design and working model will be made available by enacting the Release to Public policies of Mae Fah Luang University. We plan to package our algorithm in an Orange module as well as a self-contained software complete with user interface. Code will be developed using volume shadow copy technology, which will allow the recovery of prior iterations for quality control.

% \vspace{2mm}
% \noindent
% The results of the research performed under this proposal will be disseminated primarily through publication in research journals and conference presentations, subject to the user approval. All electronic data generated by proposal research will be redundantly archived.  Locally, the laboratory has a secure server on which all information is stored.  The server hard drives are set up in a RAID that is capable of full recovery even in the case of multiple simultaneous disk failure.
% Additionally, the server drives are backed up on an independent server operated by the School of Information Technology.  This will allow full recovery of data in the even of catastrophic failure of the local laboratory server. All of these systems will be in place for the 3-year minimum proscribed by the NSF, and the foreseeable future following that.

\end{document}

### 2018-08-24 impact_statement.tex
First commit

\documentclass[11pt]{article}
  \usepackage[a4paper,bindingoffset=0cm,%
              left=2cm,right=2cm,top=2cm,bottom=2cm,%
              footskip=0.5cm]{geometry}
  \usepackage[pdftex]{graphicx}
  \usepackage{multicol}
  \usepackage{enumitem}
  %\usepackage{psfig}
  \usepackage{helvet}
  \usepackage{siunitx,amsmath,amssymb}

  \usepackage{sectsty}
  \sectionfont{\fontsize{12}{15}\selectfont}
  \subsectionfont{\fontsize{11}{15}\selectfont}

  %\renewcommand*\sfdefault{phv}
  %\renewcommand{\familydefault}{\sfdefault}
  \makeatletter
  \newenvironment{tablehere}
    {\def\@captype{table}}
    {}

  \newenvironment{figurehere}
    {\def\@captype{figure}}
    {}
  \makeatother

  \begin{document}
  %\title{Broadening the impact of astronomical data handling\vspace{-2ex}}
  %\maketitle
  \setcounter{figure}{0}
  \noindent
  {\LARGE \bf From Stars to Baht: Broadening the economic impact of \\
  astronomical data handling techniques in Thailand}

  \vspace{3mm}
  \noindent
  {\LARGE \bf Pathways to Impact}
  %
  \vspace{3mm}
  \noindent
  The primary goals of the proposed project are to maximise the economic impact of our Newton-funded research and to build capacity within our research team to work with external businesses and organisations. The primary focus of the Newton project has been to use astronomical data give Thai data scientists and their students experience of handling and analysing significantly larger datasets than they had previously been exposed to. No Newton funds were requested to work with external partners, as we saw training as the first crucial step to our long term goal of developing home-grown talent to promote economic development in Thailand. In the process we have learned new skills and have researched novel databasing and machine learning techniques to overcome some of the challenges inherent to storing and analysing large, constantly-updated digital datasets. We now request GCRF funds to enable the students and staff to capitalise on these skills and adapt our techniques to increase the productivity of Thai businesses and organisations.

  \vspace{2mm}
  \noindent
  The GCRF project has been carefully designed to maximise impact on both our external partners as well as on team members. For the former, this corresponds to maximising productivity, while for the latter this is in the form of capacity building by getting exposure to working with external partners -- valuable experience for setting up future collaborations beyond the lifetime of the GCRF funding. Our overall strategy of working with a limited number of pre-identified external partners is based on maximising the impact of our team's {\it current} skills and techniques. In doing so, our resources will not be spread too thinly, enabling the team to gain a deep understanding of each partner's data and analysis needs, thereby ensuring the delivery of effective solutions. This strategy also ensures that there is already an understanding among the external partners that part of their role in the collaboration is to provide researchers and students a learning experience of working with outside clients. With the skills, techniques and experience our team will acquire from this project, we will apply for follow-on GCRF funding (from 2019) to support an open call to work with any eligible external partner. Beyond that, our team will have sufficient experience to become self-sustaining, thereby ensuring maximum impact over the long term.

  \vspace{2mm}
  \noindent
  As well as our overall strategy, we have also placed maximising impact at the forefront of each individual element of the workplan. By visiting the UK to present the outcome of their Newton-funded research to the GOTO collaboration, the Thai students involved in the project will gain valuable experience in communicating with -- what is to them -- their first external partner. This will be good training for working with the external partners during the GCRF project.\footnote{This visit was not budgeted-for in our Newton project as that earlier project's specific aim was to provide training in handling and analysing large datasets, not training in collaborating with external partners.} The networking event at the start of the project will enable our team to showcase our data handling/analysis skills and techniques, using GOTO as an example, while also enabling the external partners to describe the data and analysis needs and their desired outcome of the research. This will ensure that the whole team is aware of the needs of the external partners from the outset, not just the primary contact, thereby facilitating greater collaboration within the team leading to greater impact.

  \vspace{2mm}
  \noindent
  Maximising impact is also a major consideration in planning how we will work with the external partners throughout the period of the grant. From the team's own experience from collaborating on the Newton project, regular meetings are by the far the most effective means of making progress when designing data handling and analysis systems to meet a client's needs (in that case, the client was the GOTO collaboration). This is because the client has a better sense of what data fields are more important and/or informative than others, and this must be effectively communicated to the data scientists in order for them to design an effective database or analysis system. Usually, however, this is an iterative process that evolves over multiple meetings, which is why we have planned for fortnightly meetings throughout most of the period of the project. This also has the benefit of maximising team member's exposure to working with external partners -- valuable experience for building collaborations with larger numbers of businesses and organisations after this initial GCRF grant. Finally, we want to make sure that the data solutions we provide to our external partners are effective, which is why we will deliver versions of our systems at the start of month ten for Beta testing. After testing the systems for a month, we will ask our external partners to provide feedback and we will make modifications during months eleven and twelve to ensure we meet our external partners' needs by the end of the grant.

  \vspace{2mm}
  \noindent
  The research component of the project is to adapt and advance the databasing and machine-learning techniques we have developed during the Newton project to meet the needs of our external partners. An immediate, qualitative measure of the impact of this work will be in the form of the feedback that we receive from our external partners during the third networking event at the end of the project. Once the systems have been adopted by the external partners, we will be able to quantitatively measure the impact of our research and compare against expectations laid out during the first networking event. In the case of our business partners, this will be in terms of increased productivity (i.e., turnover or profit per hour worked), whereas in the case of the educational organisations this would be in terms student admissions or staff productivity. Clearly, these numbers will only become available some time after the end of the grant, but we are committed to obtaining them since the project may prove to be an eligible REF impact case study. We will, of course, forward this data to STFC for their own impact monitoring.

  \end{document}

### 2018-08-24 oda_statement.tex
First commit

\documentclass[11pt]{article}
  \usepackage[a4paper,bindingoffset=0cm,%
              left=2cm,right=2cm,top=2cm,bottom=2cm,%
              footskip=0.5cm]{geometry}
  \usepackage[pdftex]{graphicx}
  \usepackage{multicol}

  %\usepackage{psfig}

  \usepackage{siunitx,amsmath,amssymb}

  \usepackage{sectsty}
  \sectionfont{\fontsize{12}{15}\selectfont}
  \subsectionfont{\fontsize{11}{15}\selectfont}

  %\renewcommand*\sfdefault{phv}
  %\renewcommand{\familydefault}{\sfdefault}
  \makeatletter
  \newenvironment{tablehere}
    {\def\@captype{table}}
    {}

  \newenvironment{figurehere}
    {\def\@captype{figure}}
    {}
  \makeatother

  \begin{document}
  %\title{Broadening the impact of astronomical data handling\vspace{-2ex}}
  %\maketitle
  \setcounter{figure}{0}
  \noindent
  {\LARGE \bf From Stars to Baht: Broadening the economic impact of \\
  astronomical data handling techniques in Thailand}

  \vspace{3mm}
  \noindent
  {\LARGE \bf ODA statement}

  \vspace{2mm}
  \noindent
  With a per capita GDP of 5,907~USD in 2016 ({\it Data:} World Bank), Thailand falls firmly within the OECD's DAC list of upper middle income economies. Like most such economies, Thailand has already successfully overcome many of the greatest problems of developing countries, such as basic infrastructure development. Instead, the primary economic challenge that Thailand now faces is to transition from a middle to a high-income economy. Making this transition has proven extremely difficult for many other developing economies, with some remaining stuck in the so-called ``middle-income trap'' for decades (Agenor \& Canuto, 2012). Avoiding this trap is crucial if Thailand's recent strong economic growth is to be sustained over the long term.

  \vspace{2mm}
  \noindent
  The detailed causes and means of avoidance of the middle income trap are complex and subject to debate. However, a common theme among countries that have transitioned from middle to high-income economies during the past 50 years is a sustained increase in productivity (i.e., economic output per hour worked; Aiyar et al, 2013). In recent years it has been recognised that one of the most effective means of increasing productivity is via the scientific analysis of digital data to identify trends in, for example, customer information, patient medical records, distribution networks etc. (Bakhshi \& Mateos-Garcia, 2012). There is clear evidence, therefore, that providing Thai businesses and organisations access to the skills needed to handle and analyse large digital datasets will assist Thailand's transition to a high-income economy. This is even more pertinent in the regions outside Bangkok which have traditionally suffered from slower rates of growth (World Bank, 2017), possibly due to poorer access to high-tech skills.

  \vspace{2mm}
  \noindent
  Our team's long-term ambition is to provide Northern Thailand's businesses and organisations with home-grown talent in handling and analysing large quantities of digital data. Northern Thailand is one of the regions that have experienced weaker economic growth compared to the rest of the country (World Bank, 2017). However, as our Letters of Support demonstrate, businesses and organisations in that area are crying out for access to the data handling and analysis skills and technologies that our team can provide. If this demand is not met locally, there is the risk that they and others like them will seek these skills further afield in Bangkok or, worse, from companies not based in Thailand, to the detriment of the local economy.

  \vspace{2mm}
  \noindent
  Our first step in achieving our long-term goal has been to give Thai data scientists and their students experience in handling and analysing large, frequently-updated digital datasets of the kind produced by modern industries. This need was met through our Newton-funded project which gave the Thai team members access to large amounts of astronomical data. To date, this has been extremely successful; not only have the students acquired valuable training in ``Big Data'' analysis (as planned) but the team has also developed novel data handling and analysis technologies to overcome some of the challenges presented by this type of data; see our Case for Support. The next step in reaching our long-term goal is for the team to gain experience of working with external partners, which is the motivation for this, our first GCRF funding application. In researching how to adapt and develop our skills and technologies to the needs of our five external partners, we will have a real economic impact on parties external to our team. More importantly, it will prepare the team for the next step in our long-term plan: to work with a larger, more diverse range of businesses and organisations (this will form the basis of a follow-on GCRF funding application). That will give our team the experience necessary to reach our ultimate goal: to set up a self-sustaining ``Centre of Excellence'' for researching technologies to meet the data handling and analysis needs of businesses and organisations in Northern Thailand.

  \vspace{2mm}
  \noindent{\bf References} {\scriptsize Agenor \& Canuto, 2012, Middle-Income Growth Traps. Policy Research working paper;no. 6210. World Bank, Washington, DC. World Bank. https://openknowledge.worldbank.org/handle/10986/12004 License: CC BY 3.0 IGO.; Ayar et al, 2013, Growth Slowdowns and the Middle-Income Trap, IMF Working Paper 13/71; Bakhshi \& Mateos-Garcia, 2012, The Rise of the Datavores, www.nesta.org.uk/sites/default/files/rise\_of\_the\_datavores.pdf; World Bank, 2017, ``The World Bank in Thailand'', http://www.worldbank.org/en/country/thailand/overview\#1}

  \end{document}

### 2018-08-24 resource_justification.tex
First commit

\documentclass[11pt]{article}
  \usepackage[a4paper,bindingoffset=0cm,%
              left=2cm,right=2cm,top=2cm,bottom=2cm,%
              footskip=0.5cm]{geometry}
  \usepackage[pdftex]{graphicx}
  \usepackage{multicol}

  %\usepackage{psfig}

  \usepackage{siunitx,amsmath,amssymb}

  \usepackage{sectsty}
  \sectionfont{\fontsize{12}{15}\selectfont}
  \subsectionfont{\fontsize{11}{15}\selectfont}

  %\renewcommand*\sfdefault{phv}
  %\renewcommand{\familydefault}{\sfdefault}
  \makeatletter
  \newenvironment{tablehere}
    {\def\@captype{table}}
    {}

  \newenvironment{figurehere}
    {\def\@captype{figure}}
    {}
  \makeatother

  \begin{document}
  %\title{Broadening the impact of astronomical data handling\vspace{-2ex}}
  %\maketitle
  \setcounter{figure}{0}
  \noindent
  {\LARGE \bf From Stars to Baht: Broadening the economic impact of \\
  astronomical data handling techniques in Thailand}

  \vspace{3mm}
  \noindent
  {\LARGE \bf Justification of resources }
  \vspace{-3mm}
  \section{Directly Incurred Costs: 20,819 (all values in GBP)}
  \vspace{-3mm}
  {\bf Networking events:} We will hold three 3-day networking events in Chiang-Rai to be attended by all co-I's, students and representatives from the external partners (up to 30 people). The first is to introduce the team to the external partners and to start to understand their needs, a second after six months to discuss and finalise broad specifications of what we will deliver, and a third at the end of the project for feedback and to explore future prospects of the partnerships. Each event is costed at 2728 and covers: hotel and flight costs for 5 participants not based in Chiang-Rai (1172), transport within Chiang-Rai (234), food and drink (970) and meeting room (352). Total: 8184. {\bf Transport to partners:} We have budgeted 773 for transport to the external partners' sites during the course of the project. {\bf User training:} We will hold a six-day workshop to train the external partners in the use of our systems. For this, we have budgeted for: meeting room (703), food and drink (646), transport (609). Total: 1959. {\bf Consumables:} We request 7500 to buy a network of five high-performance computers. This is the minimum needed to produce a working distributed database on which the external partners' data can be stored and managed effectively. On this network, we will install the {\it Hadoop} databasing ecosystem - the most widely-used solution for distributed data storage, management and analytics system - and use it to both research the optimum data storage and management solutions for our external partners and to train the end users. The network will consist of 1$\times$Hadoop cluster management module (Quad-core, 32 GB RAM; 1406), 1$\times$Database service module (Quad-core, 32 GB RAM; 1406), 1$\times$Hadoop Namenode (Quad-core, 32 GB RAM; 1406), 2$\times$Hadoop Datanodes (Quad core, 64 GB RAM each; total for both 3281). {\bf Outreach:} At the end of the project, we will host an outreach event in a public space (e.g., shopping mall) to demonstrate to the public and other businesses (i.e., potential future partners) the benefits of science in general and data science specifically. Total: 2403

  \vspace{-3mm}
  \section{Investigator Effort: 41,250}
  \vspace{-3mm}
  {\bf Thai salaries:} There are seven Thai co-Is on the grant, six of which we request 0.2FTE each. We request an extra 0.2FTE for Dr. Boongoen to account for his managerial role on the project (resulting in 0.4FTE for him). The 0.2FTE is justified on the basis that all co-I's will attend the 3-day networking events (plus 1 day each to assist with organising the events) and the six-day workshop (18 days total). Each Thai co-I is then required to commit the equivalent of 1 day per fortnight to the project (24 days). This corresponds to 0.18FTE, which we round to 0.2FTE to cover any extra time spent on the project. Total: 23598 {\bf UK FEC:} Following the same justification, we request 0.2FEC for Mullaney (salary, NI, pension, Estates, Indirect costs), of which STFC will cover 80\%. Total STFC contribution: 17652

  \vspace{-3mm}
  \section{Indirect and Estate costs at Thai Institutions: 4,720}
  \vspace{-3mm}
  As stipulated in the guide, this is calculated at a rate of 20\% of the total Thai investigator salaries.

  \vspace{-3mm}
  \section{Travel and subsistence: 6,568}
  \vspace{-3mm}
  {\bf Thai co-Is/researchers:} We request 1000 per person to cover the costs of return flights from Thailand to the UK for two research students to visit the GOTO collaboration for one week. We also request 100 per person per day for hotels and subsistence. Total: 3400 {\bf UK PI:} We request 1000 for each return flight for Mullaney to attend each networking event. Mullaney's accommodation and subsistence during the event are already included in the direct costs. Mullaney will stay for a further four nights after each event, for which we request accommodation and subsistence costs of 80 per day. Total STFC contribution (at 80\%): 3168.

  \vspace{-3mm}
  \section{Total Request: 73,357}

  \end{document}

### 2018-08-28 case_for_support.tex
Edited case for support

@@
   \noindent
-  {\large \bf 1.1 Background: Using astronomy data to train Thai data scientists}
+  {\large \bf 1.1 Background}
 
@@
 
-  Facilitated by STFC funding via the Newton and GCRF programs our team of educators and researchers are developing a highly effective data science training programme for Thai students.
-As part of this programme, students work with external industries and organisations to gain first-hand experience in using data science to solve real-world problems.
-The first students involved in our training programme developed novel machine learning-based technologies to identify rare true positive sources within astronomy datasets which contained a much larger (i.e., by a factor of $>1000$) samples of false positives; an example of a heavily imbalanced dataset that off-the-shelf machine learning algorithms struggle to deal with.
+  Facilitated by STFC funding via the Newton and GCRF programs (details below) our team of educators and researchers are developing a highly effective data science training programme for Thai students.
+Within this programme, students work with external research organisations and businesses to gain first-hand experience of using data science to solve real-world problems.
+To date, this programme has been highly productive, as evidenced by:
+  \begin{itemize}
+    \item two students presenting peer-reviewed proceedings at three international conferences (one of whom was awarded a ``Best Presentation'' prize);
+    \item the publication of five peer-reviewed journal articles or conference proceedings;
+    \item successfull collaborations with five external business at the regional level;
+    \item keen interest from five national businesses to join our collaboration.
+  \end{itemize}
+  By building on these sucesses and expanding our external partnerships to a national level, the next phase of our project will establish MFU as a hub for data science research and training within northern Thailand.
+This will enable future students, businesses and organisations to benefit indefinitely from STFC's present investment.
 
-  events within astronomy
+  The collaboration between the PIs (based at Sheffield and MFU) started in February, 2017, with a 12-month Newton-funded project in which Thai data scientists in our team worked with Thai graduate students to develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO).
+GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}.
+This large, constantly-updated dataset gave the students involved in that first phase the opportunity to develop the skills and techniques needed to handle and analyse the kinds of Big Data generated by many of today's industries.
+Following this first phase of the project, we were awarded a further two years' of Newton funding from February 2018 to continue our work with GOTO.
 
-  As a consequence of STFC funding (via the GCRF and Newton programs) our team of educators and researchers have been
-
-  Since February, 2017, our team of educators and researchers from multiple disciplines and institutions have been
-
-  However, Thai data scientists and their students typically lack access to very large amounts of digital data, restricting their training in ``Big Data'' science that is so crucial for the development of modern economies.
-To address this problem, we successfully applied for Newton funding (12-month project starting February, 2017) to give the Thai data scientists in our team research experience of working with large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO).
-GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}.
-This large, constantly-updated dataset has given our research team the opportunity to develop the skills and techniques needed to handle and analyse the kinds of Big Data generated by many of today's industries.
-
-  \vspace{2mm}
-  \noindent
-  The primary {\it research} goals of our Newton project were to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated Machine-Learning (ML) algorithms capable of quickly and robustly categorising sources detected by GOTO.
+  The primary {\it research} goals of our ongoing Newton project are to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated Machine-Learning (ML) algorithms capable of quickly and robustly categorising sources detected by GOTO.
 Our research has led to some novel solutions.
@@
   \noindent
-  At present, the impact of our Newton project is limited to the people directly involved in the project (i.e., Thai and UK astronomers, Thai data scientists and their students), whereas our long-term ambition has always been to broaden the impact of our research to develop the wider Thai economy.
-In this regard the goal of this GCRF project is to use the technology and skills we have developed to increase the productivity of Thai businesses and organisations.
-To do this effectively, our team needs to first gain experience of working with such external parties to research how best to adapt our technologies and expertise to their data handling and analysis needs.
+  During the first phase of our Newton-funded project, it became clear that the technologies we are developing and the training we are providing would be of great use to a broad range of organisations and businesses within Thailand.
+With this in mind, we successfully applied to STFC's 2017 GCRF funding call to fund research into how we could adapt the technology and training we have developed to increase the productivity of Thai businesses and organisations.
+Through this project, our researchers and students have gained experience of working with five such external partners, and have been praised for their achievements so far (see support letter from Thanapiriya).
 
@@
   \noindent
-  For this partnership-building project, we request funds to research how our data archiving and analysis techniques can be adapted to meet the needs of five pre-identified Thai businesses and organisations (hereafter, ``external partners''; see Table 1).
-All our external partners are based in areas local to the Thai co-Is and have already agreed to work with us throughout the 12-month project (see Letters of Support).
-At this ``capacity building'' stage, we prefer to limit the number of external partners as it ensures that all parties have a thorough understanding of the goals and expectations of the project from the outset.
-In addition to our research goals, our aim is to learn lessons and define commonalities of approach that can be applied when we expand the project to work with larger numbers of external partners.
-Our ambition is to apply for follow-on GCRF funding to support this expansion.
+  Our work funded through the round of GCRF funding has demonstrated our ability to successfully collaborate with external organisations.
+Our current external partners have a regional, as opposed to national or international, presence.
+While working with such small-to-medium size partners has proven beneficial in terms of our developing good working relationships, our ultimate goal is to also work with partners with a national presence within Thailand.
+Doing so will provide MFU with the exposure needed to become self-sustaining in terms of attracting a broad variety of external partners to work with our team and their students.
+
+  For this capacity-building project, we request funds to expand upon our first GCRF-funded project to work with four further external partners, each of which have a more national presence than the partners involved with the first phase.
+We also request funding to continue our collaboration with Thanapiriya.
+All our external partners have already agreed to work with us throughout the 24-month project (see Letters of Support).
+At the end of the first 12 months, however, we plan to hold a networking event to attract other external partners.
 

### 2018-08-28 case_for_support.tex
Finished two partners

@@
   \noindent
-  Our work funded through the round of GCRF funding has demonstrated our ability to successfully collaborate with external organisations.
+  Our work funded through the first round of GCRF funding has demonstrated our ability to successfully collaborate with external organisations.
 Our current external partners have a regional, as opposed to national or international, presence.
@@
 All our external partners have already agreed to work with us throughout the 24-month project (see Letters of Support).
-At the end of the first 12 months, however, we plan to hold a networking event to attract other external partners.
+At the end of the first 12 months, however, we will hold a networking event to attract other external partners.
+Below, we provide a brief description of the external partners and their data needs:
+
+  \begin{itemize}
+  \item {\bf Thai AirAsia} is part of the AirAsia group, which is the largest budget airline operating in South East Asia.
+They are renowned among the air industry for their high levels of aircraft utility (i.e., maximising the time a plane is in the air, and thus generating revenue).
+A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while they wait for the delivery of spare parts from various warehouses.
+This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement, and then act upon this when the aircraft was located at an airport with a parts warehouse.
+AirAsia engineers will share their flight data with our team so that we can adapt the techniques we have developed to identify rare sources in astronomy to better predict rare instances where parts require replacement.
+To assist with this development, Thai AirAsia have offered to host the students working on the project on a work-experience placement.
+  \item {\bf Thaweeyont} is a chain of bricks-and-mortar stores that specialise in electronic household appliances, furniture and motorcycles/scooters.
+They have expanded rapidly over the past decade, and are now looking to move into more locations.
+A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store.
+Thaweeyont would like a work with small group of students and researchers to investigate how we can adapt the work conducted during the first phase of our GCRF project (see Thanapiriya) to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
+  \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand.
+\end{itemize}
 

### 2018-08-29 case_for_support.tex
Added hotel chain

@@
 To assist with this development, Thai AirAsia have offered to host the students working on the project on a work-experience placement.
-  \item {\bf Thaweeyont} is a chain of bricks-and-mortar stores that specialise in electronic household appliances, furniture and motorcycles/scooters.
-They have expanded rapidly over the past decade, and are now looking to move into more locations.
+  %\item {\bf Thaweeyont} is a chain of bricks-and-mortar stores that specialise in electronic household appliances, furniture, and motorcycles/scooters.
+They have expanded rapidly over the past decade, and are now looking to expand into more locations.
 A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store.
@@
   \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand.
+This region is a popular tourist destination, resulting in a particularly competitive hotel market and corresponding thin margins.
+Deevana has found that various promotions (e.g., reduced tariffs, free services/experiences, etc.) help boost traffic to their hotels, resulting in fewer empty rooms.
+At present, however, they use a scatter-gun approach to advertise these promotions, whereas more targeted campaigns based on customer need may deliver better results.
+Deevana wishes for our students to research how machine learning -- in particular clustering analysis -- could be used to better identify different types of customers and test which promotions are most effective at attracting different customer types.
+In return, our staff and students will gain experience in a developing technology solutions for one of Thailand's most important economic sectors.
+  \item {\bf Biophics} is a Center of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok.
+They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand.
 \end{itemize}

### 2018-08-29 case_for_support.tex
Finished partner profiles

@@
     \item successfull collaborations with five external business at the regional level;
-    \item keen interest from five national businesses to join our collaboration.
+    \item keen interest from four national businesses to work with us in solving their data handling and analysis needs.
   \end{itemize}
@@
   \noindent
-  {\large \bf 1.2 Broadening the impact of our research to local businesses and organisations}
+  {\large \bf 1.2 Broadening the impact of our research to national businesses and organisations}
 
@@
 To assist with this development, Thai AirAsia have offered to host the students working on the project on a work-experience placement.
-  %\item {\bf Thaweeyont} is a chain of bricks-and-mortar stores that specialise in electronic household appliances, furniture, and motorcycles/scooters.
+  \item {\bf Thanapiriya} is a chain of supermarkets spread across various locations in Northern Thailand.
 They have expanded rapidly over the past decade, and are now looking to expand into more locations.
 A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store.
-Thaweeyont would like a work with small group of students and researchers to investigate how we can adapt the work conducted during the first phase of our GCRF project (see Thanapiriya) to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
+Thanapiriya was one of the partners involved in our first GCRF project and would like to continue to work with us.
+They would like to work with small group of students and researchers to investigate how we can adapt the work conducted during the first phase of our GCRF project to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
   \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand.
@@
 They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand.
+Biophics would like to work with our students on developing a ML-based algorithm to identify outliers in Tuberculosis (TB) patient records that may help to identify instances of drug resistance.
+This is a ``rare event'' problem similar to the one we have developed solutions to for analysing GOTO data.
+Being part of Mahidol University -- Thailand's top-ranked medical school -- Biophics is highly familiar with the anonymisation of patient data to the levels required by Thai law, and no patient data will be shared outside Thailand.
+  \item {\bf OpenLandscape} is a provider of cloud computing infrastructure in Thailand.
+As in western economies, it is predicted that many Thai companies will switch to rented cloud-based infrastructure from in-house computer hardware.
+In order to grow, OpenLandscape needs to attract more customers, but also be able to predict when those customers will place greatest load on their systems.
+To help achieve these aims, OpenLandscape would like to work with a group of students to (a) analyse their customer database and usage logs to classify customers according to their usage type, which they will use to target potential customers with bespoke promotions and; (b) analyse the the usage logs of their hardware to predict when those times when there is heaviest load on their systems.
+Working with OpenLandscape will provide the students involved in the project with experience in one of Thailand's fastest growing industries.
 \end{itemize}
 
-  \begin{table}[h]
-  \begin{tabular}{p{2.8cm}|p{13.4cm}}
-    {\it Partner} & {\it Data handling/analysis needs}\\
-    \hline
-    \hline
-      Thanapiriya plc & A food retail business that wishes to take multiple factors into account to predict optimum stock volumes.
-This is a categorisation problem (the same type faced with GOTO data) in terms of increase/decrease/no-change of product demand.\\
-    \hline
-      TAPP Auto & A car sales business seeking to develop a system that can predict the depreciation curve of a given vehicle given multiple input factors.
-This is a regression and ``missing data'' problem, as commonly found in astronomy data analysis.\\
-    \hline
-       Pibulsongkram Raj.
-University & The Academic Resources Office wishes to identify the optimum online resources to meet the needs of different types of users.
-This can be achieved through ML-based Personalised Service Provision as often used by streaming services.\\
-    \hline
-      MFU & The Student Office seeks a system to identify the causes of the high student dropout rates in Thai Universities.
-This is, in part, a categorisation problem, since students can be grouped according to different drop-out factors.
-\\
-    \hline
-      M-Store & A retail complex based on MFU's campus seeks to increase footfall by targeting promotions to specific groups.
-A ML-based clustering analysis will help to identify different categories according to customer information.
-\\
-    \hline
-  \end{tabular}
-  \caption{\it Our external partners and a brief description of their data handling and analysis needs. }
-  \vspace{-5mm}
-  \end{table}
-  \vspace{3mm}
   \noindent
@@
   \noindent
-  Over the twelve month period of the grant, we will (in broadly chronological order; see Gantt Chart):
+  Over the 24-month period of the grant, we will (in broadly chronological order; see Gantt Chart):
   \begin{enumerate}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
-  \item Have the Thai staff and students currently working on the project visit the UK.
-The purpose of this visit is provide the students with first-hand experience of presenting to and communicating with their first external partner -- the GOTO collaboration.
-  \item Host a networking event in Chiang-Rai, Thailand, where most of the Thai co-Is and external partners are based.
-All team members and representatives from all external partners will attend.
-At the event, our team will deliver a series of short presentations to highlight our skills and technology, using GOTO as a case study.
-Representatives from our external partners will describe their businesses/organisations, the data they hold, and agree with the team their desired outcomes from the project, together with an estimate of their impact.
-  \item Each external partner will be assigned at least one primary team member contact (this could be a postgraduate student, in which case a staff researcher will act as a secondary contact).
-The primary contact will attend on-site fortnightly meetings with the external partner to get to fully understand their data and analysis needs.
-Such close interaction is vital in order to discriminate between informative vs.
-non-informative data.
+  \item Host the first networking event in Chiang-Rai, Thailand (where most of the Thai co-Is are based), attended by all UK and Thai team members and representatives from all our pre-identified external partners.
+During the event, our team will deliver a series of short (5-10 minute) presentations to highlight our data-led solutions developed during the previous batch of external users, and available expertise within the team.
+Representatives from our external partners will also be asked give short presentations to describe their business/organisation and what they seek to achieve from the collaboration
+  \item Each problem will be assigned a staff researcher as a main contact, who (and other staffs) co-supervise one student group (senior-project group).
+The role of the primary contact is to have fortnightly meetings with the external partner to present results and receive feedback.
 After each meeting, the primary contact will report back to the rest of the team to ensure a collaborative effort is maintained.
-Start researching and testing possible solutions to the external partners' needs.
-  \item We will host a second networking event in month 5.
-By this stage, the team will have a thorough understanding of the data and needs of each external partner and will have researched possible solutions, enabling us to decide on the broad design of what we will deliver to each partner.
-This design will be discussed and agreed-upon by the external partners during the networking event.
+Having identified possible data, the students will visit and work with each external user for 2 weeks to ensure the quality of collected/preprocessed data, with a chance to communicate directly with the user.
+  \item By month 4 the team’s work will move to the implementation phase by increasingly focusing on adapting our technology and techniques to the needs of the users.
+During the fortnightly meetings the teams will demonstrate their solutions and allow the client to suggest improvements.
+  \item During month 7, we will host another meeting between UK and Thai team members and representatives from all external partners.
+This will allow us to revisit the tasks accomplished in the first half, specify the limitations/difficulties identified found during the past six months, and revise the working plan for the rest of the projects.
+This will include plans for further on-site visits to provide user training, and also the preparation for internships where students can help users to solve more problems.
   \item Our work will focus on delivering the agreed systems by adapting our own and further researching new techniques to meet our partners' needs.

### 2018-08-29 case_for_support.tex
Finished timeline

@@
   {\LARGE \bf Case for support}
-  \vspace{3mm}
-
-  \noindent
-  We request funds to extend our previous GCRF-funded project
-
-  research how the data archiving and analysis techniques we have developed as part of our previous STFC/Newton-funded project can be best adapted to address the needs of Thai businesses and organisations.
-To achieve this research aim, our multi-disciplinary team of Thai and UK scientists will spend 12 months working closely with a group of five pre-identified businesses and organisations based in Northern Thailand that have specific data archiving and analysis needs.
+%  \vspace{3mm}
 
@@
 
-  Facilitated by STFC funding via the Newton and GCRF programs (details below) our team of educators and researchers are developing a highly effective data science training programme for Thai students.
+  \vspace{2mm}
+  \noindent
+  Facilitated by STFC funding via the Newton and GCRF programs our team of educators and researchers are developing a highly effective data science training programme for Thai students.
 Within this programme, students work with external research organisations and businesses to gain first-hand experience of using data science to solve real-world problems.
@@
   \end{itemize}
-  By building on these sucesses and expanding our external partnerships to a national level, the next phase of our project will establish MFU as a hub for data science research and training within northern Thailand.
-This will enable future students, businesses and organisations to benefit indefinitely from STFC's present investment.
+  By building on these sucesses and expanding our external partnerships to a national level, the next phase of our project will establish Mae Fah Luang University (MFU; the Thai PI institute) as a hub for data science research and training within northern Thailand.
+This will enable future students, businesses and organisations to benefit indefinitely from STFC's investment.
 
-  The collaboration between the PIs (based at Sheffield and MFU) started in February, 2017, with a 12-month Newton-funded project in which Thai data scientists in our team worked with Thai graduate students to develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO).
+  \vspace{2mm}
+  \noindent
+  Our collaboration started in February, 2017, with a 12-month Newton-funded project.
+For this project, our team worked with Thai graduate students research and develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO).
 GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}.
-This large, constantly-updated dataset gave the students involved in that first phase the opportunity to develop the skills and techniques needed to handle and analyse the kinds of Big Data generated by many of today's industries.
+This large, constantly-updated dataset gave the students the opportunity to develop the skills and techniques needed to handle and analyse the kinds of Big Data generated by many of today's industries.
 Following this first phase of the project, we were awarded a further two years' of Newton funding from February 2018 to continue our work with GOTO.
 
-  The primary {\it research} goals of our ongoing Newton project are to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated Machine-Learning (ML) algorithms capable of quickly and robustly categorising sources detected by GOTO.
+  \vspace{2mm}
+  \noindent
+  The primary {\it research} goals of our Newton project are to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated Machine-Learning (ML) algorithms capable of quickly and robustly categorising sources detected by GOTO.
 Our research has led to some novel solutions.
-For the database component we are developing a hybrid system that combines the structure of a relational database (such at that used by SDSS) with the flexibility of a non-relational database (which are popular within tech.
-industries).
-For the ML component, we are developing a new two-stage categorisation algorithm which uses unsupervised ML algorithms to quickly remove obvious artefacts from our data before passing more ambiguous cases to a supervised ML algorithm.
+For the database component are researching whether distributed non-relational databases are an effective means of storing and analysing large astronomical datasets.
+For the ML component, we are developing effective new methods to train algorithms to identify and classify very rare transient events among tens of thousands of astronomical sources.
 Since both goals are to address challenges associated with archiving and analysing large amounts of astronomical data, the science, technology and expertise involved in the proposed GCRF project has originated from work associated with STFC's core Science Programme.
@@
   During the first phase of our Newton-funded project, it became clear that the technologies we are developing and the training we are providing would be of great use to a broad range of organisations and businesses within Thailand.
-With this in mind, we successfully applied to STFC's 2017 GCRF funding call to fund research into how we could adapt the technology and training we have developed to increase the productivity of Thai businesses and organisations.
+With this in mind, we successfully applied to STFC's 2017 call for GCRF Foundation funding to research how we could adapt the technology and training we developed during our Newton project to increase the productivity of Thai businesses and organisations.
 Through this project, our researchers and students have gained experience of working with five such external partners, and have been praised for their achievements so far (see support letter from Thanapiriya).
@@
   \noindent
-  Our work funded through the first round of GCRF funding has demonstrated our ability to successfully collaborate with external organisations.
-Our current external partners have a regional, as opposed to national or international, presence.
-While working with such small-to-medium size partners has proven beneficial in terms of our developing good working relationships, our ultimate goal is to also work with partners with a national presence within Thailand.
-Doing so will provide MFU with the exposure needed to become self-sustaining in terms of attracting a broad variety of external partners to work with our team and their students.
+  Our GCRF-funded project has demonstrated our ability to successfully collaborate with external organisations.
+Presently, our external partners have a regional, as opposed to national or international, presence.
+While working with these small-to-medium sized businesses and organisations has provided our team with invaluable experience of liasing with external partners, our long-term goal is to also work with partners with a national presence within Thailand.
+Doing so will provide MFU with the exposure needed to become self-sustaining in terms of attracting a variety of future external partners.
 
-  For this capacity-building project, we request funds to expand upon our first GCRF-funded project to work with four further external partners, each of which have a more national presence than the partners involved with the first phase.
-We also request funding to continue our collaboration with Thanapiriya.
+  \vspace{2mm}
+  \noindent
+  For this capacity-building project, we request funds to expand upon our GCRF Foundation Award-funded project to work with four further external partners, each of which have a more national presence than the partners involved with the our Foundation project.
+We also request funding to continue our successful collaboration with Thanapiriya -- the largest of our first partners.
 All our external partners have already agreed to work with us throughout the 24-month project (see Letters of Support).
@@
 
-  \begin{itemize}
+  \begin{itemize}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
     \item {\bf Thai AirAsia} is part of the AirAsia group, which is the largest budget airline operating in South East Asia.
-They are renowned among the air industry for their high levels of aircraft utility (i.e., maximising the time a plane is in the air, and thus generating revenue).
-A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while they wait for the delivery of spare parts from various warehouses.
-This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement, and then act upon this when the aircraft was located at an airport with a parts warehouse.
-AirAsia engineers will share their flight data with our team so that we can adapt the techniques we have developed to identify rare sources in astronomy to better predict rare instances where parts require replacement.
-To assist with this development, Thai AirAsia have offered to host the students working on the project on a work-experience placement.
+They are renowned among the air industry for their high levels of aircraft utility.
+A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while they wait for the delivery of spare parts.
+This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement.
+AirAsia engineers will share their flight data with the students working on this project so that we can adapt the technologies we have developed to better predict when parts will require replacement.
     \item {\bf Thanapiriya} is a chain of supermarkets spread across various locations in Northern Thailand.
@@
 A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store.
-Thanapiriya was one of the partners involved in our first GCRF project and would like to continue to work with us.
-They would like to work with small group of students and researchers to investigate how we can adapt the work conducted during the first phase of our GCRF project to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
+Their aim is to work with a small group of students and researchers to research effective means to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
     \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand.
-This region is a popular tourist destination, resulting in a particularly competitive hotel market and corresponding thin margins.
-Deevana has found that various promotions (e.g., reduced tariffs, free services/experiences, etc.) help boost traffic to their hotels, resulting in fewer empty rooms.
-At present, however, they use a scatter-gun approach to advertise these promotions, whereas more targeted campaigns based on customer need may deliver better results.
+Deevana use promotions help attract guests to their hotels.
+At present they use a scatter-gun approach to advertise these promotions, whereas they would like to investigate whether more targeted campaigns based on customer need can deliver better results.
 Deevana wishes for our students to research how machine learning -- in particular clustering analysis -- could be used to better identify different types of customers and test which promotions are most effective at attracting different customer types.
-In return, our staff and students will gain experience in a developing technology solutions for one of Thailand's most important economic sectors.
     \item {\bf Biophics} is a Center of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok.
 They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand.
-Biophics would like to work with our students on developing a ML-based algorithm to identify outliers in Tuberculosis (TB) patient records that may help to identify instances of drug resistance.
+Biophics would like to work with our students to develop a ML-based algorithm to identify outliers in Tuberculosis (TB) patient records that may help to identify instances of drug resistance.
 This is a ``rare event'' problem similar to the one we have developed solutions to for analysing GOTO data.
-Being part of Mahidol University -- Thailand's top-ranked medical school -- Biophics is highly familiar with the anonymisation of patient data to the levels required by Thai law, and no patient data will be shared outside Thailand.
-  \item {\bf OpenLandscape} is a provider of cloud computing infrastructure in Thailand.
-As in western economies, it is predicted that many Thai companies will switch to rented cloud-based infrastructure from in-house computer hardware.
-In order to grow, OpenLandscape needs to attract more customers, but also be able to predict when those customers will place greatest load on their systems.
-To help achieve these aims, OpenLandscape would like to work with a group of students to (a) analyse their customer database and usage logs to classify customers according to their usage type, which they will use to target potential customers with bespoke promotions and; (b) analyse the the usage logs of their hardware to predict when those times when there is heaviest load on their systems.
-Working with OpenLandscape will provide the students involved in the project with experience in one of Thailand's fastest growing industries.
+    \item {\bf OpenLandscape} is a provider of cloud computing infrastructure and services in Thailand.
+In order to grow, OpenLandscape needs to attract customers, but also be able to predict when those customers will place greatest load on their systems.
+OpenLandscape would like to work with a group of our students to (a) analyse their customer database and usage logs to classify customers according to their usage type, which they will use to target potential customers with bespoke promotions and; (b) analyse the usage logs of their hardware to predict those times when there is heaviest load on their systems.
   \end{itemize}
+  %Being part of Mahidol University -- Thailand's top-ranked medical school -- Biophics is highly familiar with the anonymisation of patient data to the levels required by Thai law, and no patient data will be shared outside Thailand
+  \noindent
+  {\large \bf 1.3 Description of work to be undertaken}
 
   \noindent
-  {\large \bf 1.3 Description of work to be undertaken}
+  {\bf 1.3.1 Working with external partners}
 
@@
   \item Host the first networking event in Chiang-Rai, Thailand (where most of the Thai co-Is are based), attended by all UK and Thai team members and representatives from all our pre-identified external partners.
-During the event, our team will deliver a series of short (5-10 minute) presentations to highlight our data-led solutions developed during the previous batch of external users, and available expertise within the team.
-Representatives from our external partners will also be asked give short presentations to describe their business/organisation and what they seek to achieve from the collaboration
-  \item Each problem will be assigned a staff researcher as a main contact, who (and other staffs) co-supervise one student group (senior-project group).
-The role of the primary contact is to have fortnightly meetings with the external partner to present results and receive feedback.
-After each meeting, the primary contact will report back to the rest of the team to ensure a collaborative effort is maintained.
-Having identified possible data, the students will visit and work with each external user for 2 weeks to ensure the quality of collected/preprocessed data, with a chance to communicate directly with the user.
-  \item By month 4 the team’s work will move to the implementation phase by increasingly focusing on adapting our technology and techniques to the needs of the users.
-During the fortnightly meetings the teams will demonstrate their solutions and allow the client to suggest improvements.
+At the event, our team will deliver a series of short (5-10 minute) presentations to highlight our data-led solutions developed during the first GCRF-funded project.
+Representatives from our external partners will be asked to describe their business/organisation and what they seek to achieve from the collaboration
+  \item Each partner will be assigned a staff researcher as a main contact, who will also lead the supervision of a group of final-year project students.
+The role of the primary contact is to coordinate fortnightly meetings with the external partner to provide progress updates and receive feedback.
+Within the first three months of the project, the students will visit and work with each external user for at least 2 weeks to ensure they fully understand the data and problem.
+  \item Around month 4 each team's will transition to the implementation phase by increasingly focusing on adapting our technology and techniques to the needs of the external partners.
+During the fortnightly meetings the teams will demonstrate their solutions and encourage the client to suggest improvements.
   \item During month 7, we will host another meeting between UK and Thai team members and representatives from all external partners.
-This will allow us to revisit the tasks accomplished in the first half, specify the limitations/difficulties identified found during the past six months, and revise the working plan for the rest of the projects.
-This will include plans for further on-site visits to provide user training, and also the preparation for internships where students can help users to solve more problems.
-  \item Our work will focus on delivering the agreed systems by adapting our own and further researching new techniques to meet our partners' needs.
+This will allow us to revisit the tasks accomplished in the first half, specify the limitations/difficulties identified during the past six months, and revise the working plan for the rest of the projects.
+Plans will be made for further on-site visits and internships.
+  \item Our work will focus on delivering the agreed systems by adapting our own and further researching new technnologies to meet our partners' needs.
 As this happens, the purpose of the fortnightly meetings will progressively shift toward feedback sessions, during which the primary contact will demonstrate our systems and allow the end user to suggest improvements.
-  \item At the start of month ten, we will deliver ``Beta versions'' of the systems we have developed.
-We will train the external partners on how to use the systems and collect any immediate feedback they may have.
-The systems will then go through a two month-long Beta testing phase by the external partners, who will then report their experience back to the team.
-During months eleven and twelve we will address any feedback from the Beta testing phase to deliver the final product.
-  \item We will host a final networking event to discuss the outcomes, successes/drawbacks, impact-to-date, and future directions of the research and partnerships.
-This event will coincide with an outreach event to highlight to the public and invited representatives from other businesses/organisations the economic benefits of data science.
-Part of the goal of this event is to identify future partnerships.
+  \item By month ten, the team will deliver “beta versions” of our solutions.
+At this time, with the use of new virtual classroom at MFU, the team will train the end user on how to use the systems and collect any immediate feedback they may have.
+Following feedback, students will work on delivering the final products by month twelve.
+  \item We will hold a networking event in month 12 to discuss the outcomes, successes/drawbacks, impact-to-date, and future directions of the research and partnerships.
+This event will be attended by other potential partners to work with a new cohort of final-year students during months 13-24.
   \end{enumerate}
-
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \vspace{3mm}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \noindent
-  {\large \bf 1.4 Maximising the impact of the project}
-
-  \noindent
-  The steps we have taken to ensure that the project has maximal impact are described fully in our Pathways to Impact statement.
-Briefly, our choice of working very closely with a limited number of external partners is motivated by our desire to focus our efforts to ensure maximal impact in terms of our partners' productivity {\it and} building our team's capacity for working with external partners.
-This experience will establish protocols and ways of working to be taken forward to future partnerships.
 
@@
   \noindent
-  In addition to the impact within Thailand, the project promises secondary benefits to UK research.
-With STFC's involvement in forthcoming data-intensive projects such as the LSST and SKA, it is vitally important that UK astronomers gain exposure to advanced data handling and analysis techniques.
-Further, the proposed work will give the team experience of working with data-intensive businesses -- valuable preparation for research supported by the UK Government's Industrial Strategy.
+  {\bf 1.3.2 Development of a Thai MOOC}
 

### 2018-08-31 case_for_support.tex
Finished management plan

@@
   \noindent
-  {\bf 1.3.2 Development of a Thai MOOC}
+  {\bf 1.3.2 Development of a Thai data science MOOC}
+
+  \noindent
+  With our partnerships with external organisations and businesses, we are able to provide world-class training in data science to Thai students enrolled at MFU, who can then take these skills to the workplace.
+However, this neglects the tens of thousands of other Thai citizens who could benefit from these skills, not least those already in full-time employment who are unable to take time off to attend University.
+The development in recent years of the Massive Open Online Course (MOOC) enables higher education institutes to greatly increase the impact of their teaching.
+
+  \vspace{2mm}
+  \noindent
+  During the final 18 months of the funded project, our team will draw upon our broader teaching experience to develop a series of data science MOOCs.
+Crucially, we will use our unique collaborations with our external partners when developing these course.
+We will consult our partners during the design process to ensure that the course both meet the skills gaps that they have identified within the Thai workforce, while also ensuring that the courses are accessible to current and potential employees.
+On successful completion of the course, participants will have the opportunity to attend one of four workshops that we will hold at MFU during that final 7 months of the project.
+The aim of this workshop will be to enable participants to collaborate with members of our team to apply the technologies they have learned during the MOOC to solve either their own data-related problems, or one of a suite of pre-defined problems using our team's own data.
+
+  \pagebreak
 
@@
   \noindent
-  The success of each external partnership will be a team effort.
-During and following the first networking event we will set out a series of milestones to reach in order to achieve each partner's desired outcome.
-After consulting with the rest of the team, Drs.
-Boongoen and Mullaney will assign primary contacts by matching team members' skills and experience to the needs of the external partners.
-Dr.
+  Our management plan for this next phase will build upon the successes of and lessons learned during the first, Foundation Award-funded, phase of the project.
+Following the success of the initial networking event at MFU, we will hold the same again at the start of this second phase.
+Prior to the networking event, teams consisting of at least one member of staff and 2-3 final year project students will be assigned to each external partner.
+During the networking event, the staff and students will speak with the external partners to gain a deeper understanding of the partners' data and desired outcome of the project (i.e., the ``problem'' they want solving).
+Our choice of using teams of 2-3 final-year students is based on our experiences from the first phase, in which larger teams of less experiences students were involved in the project.
+Unfortunately, we found that this first approach led to some students feeling less engaged with the project than others.
+By contrast, the model of using smaller groups of final-year students we have employed in our Newton-funded project has led to high levels of student engagement, so we will follow that same set-up here.
+
+  \vspace{2mm}
+  \noindent
+  Following the initial networking meeting, Dr.
 Boongoen will coordinate the fortnightly partner meetings.
@@
 The design can still evolve after this stage, but this approach ensures any evolution will be managed.
-There is the risk that an external partner may be unsatisfied with the proposed design of the Beta system.
+
+  \vspace{2mm}
+  \noindent
+  In a departure from the model adopted during the first phase, after the second networking event the students will have the opportunity to spend a limited amount of time (up to 2 weeks) as an intern based at the external partners (to which all partners have already agreed).
+The goal of the internships is two-fold: firstly, it will constitute a period of daily communication between students and partners, enabling rapid advances in product development to be made according to the partners' requirements and, secondly, give the students first-hand experience of working in industry.
+
+  \vspace{2mm}
+  \noindent
+  At any time during the project there is, of course, the risk that an external partner may be unsatisfied with the proposed design of the system.
 If that happens, it will be the responsibility of Drs.

### 2018-09-04 case_for_support.tex
Edited case for support

@@
 
-  \vspace{3mm}
+  \pagebreak
   \noindent
@@
   \noindent
-  Our multi-disciplinary team of researchers is made up of astronomers, computer and data scientists, a computer hardware specialist, and a Lecturer in Business Management and Marketing.
+  Our multi-disciplinary team of researchers is made up of astronomers, computer and data scientists, computer hardware specialists, a Lecturer in Business Management and Marketingn, and a Sales and Marketing Consultant (pro bono).
 The UK PI (Mullaney) is an astronomer with extensive experience of analysing data from large astronomical surveys.
-He was the UK PI of our Newton-funded project, responsible for ensuring that the research meets the needs of the GOTO collaboration.
+He was the UK PI of our Newton-funded and GCRF Foundation Award-funded projects.
 The Thai PI (Boongoen) is a computer scientist with specialist expertise in developing ML algorithms.
-He has extensive experience in managing research projects, having PI'd four successful grants in the last four years.
+Prior to joining MFU, Dr.
+Boongoen worked was a member of the Thai Royal Air Force working on Big Data Analytics with a particular emphasis on security applications.
+He has extensive experience in managing research projects, having PI'd six successful grants in the last five years.
 Dr.
 Iam-on is data scientist with expertise in database design, data mining, and developing ML algorithms for automated data analysis.
-She will oversee the database design elements of the project as well as contributing her expertise on the automated analysis aspect.
+Together with Arwatchananukul, Dr.
+Iam-On will oversee the database design elements of the project as well as contributing her expertise on the automated analysis aspects.
+Drs.
+Kirimasthong and Sigpant's expertise are also in the development of ML-based algorithms, which they will bring to bear as team leaders on the project.
+Mr.
+Nobnop and Mr.
+Prommool are involved in developing MFU's MOOCS, and so will assist in this part of the project.
 Dr.
-Eungwanichayapant's background is in high energy astrophysics, with particular expertise in developing unsupervised ML algorithms to analyse data from Gamma Ray telescopes.
-Drs.
-Sawangwit and Awiphan are astronomers based in Thailand.
-Their research expertise lies in analysing large astronomical datasets and time varying data, and thus are very relevant to the project.
-Mr.
-Vattayasak will be the team's computer hardware expert: his specialism is in setting up distributed networks of computers to host large, distributed databases.
-Finally, Ms.
-Noichankgkid is a Lecturer in Business Management and Marketing, with extensive management and finance experience prior to and during her academic career.
-Her experience will prove invaluable when liaising with and establishing the needs of our business partners.
+Wongwatkit's interests focus on the use of new technologies to enhance learning, and so will be particularly relevant in the latter stages of the project when developing the MOOCs and training the employees of the partners to use the systems we develop.
+Dr.
+Nupap will bring her experience as a consultant to several Thai businesses to help liaise between the researchers and external partners.
+Dr.
+Kurubanjerdjit has published research papers in the field of bioinformatics and has helped to develop secure databases to store medical information.
+As such, she will be closely involved in the Biophics project.
+Finally, Mr.
+Thongjua has over 20 years experience in Sales and Marketing, and has agreed to work with us on a pro bono basis to use his business network to identify and attract future partners.
 

### 2018-09-04 data_management.tex
Edited other docs

@@
 \noindent
-Because of their potentially commercially sensitive nature, any data transferred between the external partners and our team will be done so in an encrypted state (whether by physical media such as USB stick or over the internet).
+The main risk associated with handling data from most of our external partners is their potentially commercially sensitive nature.
+To mitigate the risk of data loss during transfer from the partners to our servers, all data will be transferred in an encrypted state (whether by physical media such as USB stick or over the internet).
 Once on site at MFU, the raw data will immediately be backed-up on MFU's multiple backup servers.
-Once this has been done, raw data will be sent (via ssh, which is encrypted once the connection is established) to the UK to be backed up on Sheffield's secure servers.
-A Structured Query Language (SQL) database will be created to track all digital files.
+One of our external partners, Biophics, stands out in terms of data risk due to the sensitive medical data that they hold.
+Biohpics is based within the Faculty of Tropical Medicine at Mahidol University, the top ranked University within Thailand to study medicine.
+As such, its members of staff are extremely well-versed in Thailand's legislation surrounding the sharing of medical records.
+They have assured us, including within their letter of support, that all data will be fully anonymised to prevent any possible identification of individuals.
 
@@
 \noindent
-Once the original raw data are backed-up on both sites, work will start on researching the best means to incorporate the data into a distributed non-relational database.
+Once the original raw data are backed-up, work will start on researching the best means to incorporate the data into a distributed non-relational database.
 The data management system we will use for this is {\it Hadoop}, which is widely used throughout the IT sector, thus ensuring the long-term readability of the data.
@@
 By signing the Letter of Support, our external partners already have an understanding of this.
-Where not commercially sensitive, all raw data will be made publicly available, together with any non-commercially sensitive derived data.
-This includes data from Pibulsongkram Rajabhat University (User behaviour and service provision) and MFU (Academic and educational development office and M-Store).
+Where possible (and after full consultation with the external partners), raw data will be made publicly available, together with any non-commercially sensitive derived data.
 

### 2018-09-04 impact_statement.tex
Finished management plan
Edited other docs

@@
   {\LARGE \bf Pathways to Impact}
-  %
+
   \vspace{3mm}
   \noindent
-  The primary goals of the proposed project are to maximise the economic impact of our Newton-funded research and to build capacity within our research team to work with external businesses and organisations.
+  The primary goals of the proposed project are to expand the economic impact of our previous GCRF-funded research and to build capacity within our research team to work with a broad variety of external businesses and organisations.
 The primary focus of the Newton project has been to use astronomical data give Thai data scientists and their students experience of handling and analysing significantly larger datasets than they had previously been exposed to.
@@
 In the process we have learned new skills and have researched novel databasing and machine learning techniques to overcome some of the challenges inherent to storing and analysing large, constantly-updated digital datasets.
-We now request GCRF funds to enable the students and staff to capitalise on these skills and adapt our techniques to increase the productivity of Thai businesses and organisations.
+Our follow-up GCRF Foundation Award has enabled us to work successfully with a small number of local businesses, during which we have demonstrated our ability to engage students in working with external partners.
+We now request follow-on GCRF funding to fully capitalise on our skills and experiences to ensure that MFU becomes a self-sustaining centre for data analytics within Thailand.
 
@@
 This strategy also ensures that there is already an understanding among the external partners that part of their role in the collaboration is to provide researchers and students a learning experience of working with outside clients.
-With the skills, techniques and experience our team will acquire from this project, we will apply for follow-on GCRF funding (from 2019) to support an open call to work with any eligible external partner.
-Beyond that, our team will have sufficient experience to become self-sustaining, thereby ensuring maximum impact over the long term.
 
@@
   As well as our overall strategy, we have also placed maximising impact at the forefront of each individual element of the workplan.
-By visiting the UK to present the outcome of their Newton-funded research to the GOTO collaboration, the Thai students involved in the project will gain valuable experience in communicating with -- what is to them -- their first external partner.
-This will be good training for working with the external partners during the GCRF project.\footnote{This visit was not budgeted-for in our Newton project as that earlier project's specific aim was to provide training in handling and analysing large datasets, not training in collaborating with external partners.} The networking event at the start of the project will enable our team to showcase our data handling/analysis skills and techniques, using GOTO as an example, while also enabling the external partners to describe the data and analysis needs and their desired outcome of the research.
+The networking event at the start of the project will enable our team to showcase our data handling/analysis skills and techniques, using GOTO as an example, while also enabling the external partners to describe the data and analysis needs and their desired outcome of the research.
 This will ensure that the whole team is aware of the needs of the external partners from the outset, not just the primary contact, thereby facilitating greater collaboration within the team leading to greater impact.
@@
   Maximising impact is also a major consideration in planning how we will work with the external partners throughout the period of the grant.
-From the team's own experience from collaborating on the Newton project, regular meetings are by the far the most effective means of making progress when designing data handling and analysis systems to meet a client's needs (in that case, the client was the GOTO collaboration).
+From the team's own experience from collaborating on our Newton and prior GCRF projects, regular meetings are by the far the most effective means of making progress when designing data handling and analysis systems to meet a client's needs.
 This is because the client has a better sense of what data fields are more important and/or informative than others, and this must be effectively communicated to the data scientists in order for them to design an effective database or analysis system.
@@
   \noindent
-  The research component of the project is to adapt and advance the databasing and machine-learning techniques we have developed during the Newton project to meet the needs of our external partners.
+  The research component of the project is to adapt and advance the databasing and machine-learning techniques we have developed so far to meet the needs of our external partners.
 An immediate, qualitative measure of the impact of this work will be in the form of the feedback that we receive from our external partners during the third networking event at the end of the project.

### 2018-09-04 oda_statement.tex
Edited other docs

@@
 To date, this has been extremely successful; not only have the students acquired valuable training in ``Big Data'' analysis (as planned) but the team has also developed novel data handling and analysis technologies to overcome some of the challenges presented by this type of data; see our Case for Support.
-The next step in reaching our long-term goal is for the team to gain experience of working with external partners, which is the motivation for this, our first GCRF funding application.
-In researching how to adapt and develop our skills and technologies to the needs of our five external partners, we will have a real economic impact on parties external to our team.
-More importantly, it will prepare the team for the next step in our long-term plan: to work with a larger, more diverse range of businesses and organisations (this will form the basis of a follow-on GCRF funding application).
-That will give our team the experience necessary to reach our ultimate goal: to set up a self-sustaining ``Centre of Excellence'' for researching technologies to meet the data handling and analysis needs of businesses and organisations in Northern Thailand.
+Our GCRF Foundation Award enabled our team to gain experience of working with external partners, which is already having a real economic impact on parties external to our team.
+We now request funding to support work with a larger, more diverse range of businesses and organisations.
+This will give our team the experience necessary to reach our ultimate goal: to set up a self-sustaining ``Centre of Excellence'' for researching technologies to meet the data handling and analysis needs of businesses and organisations in Northern Thailand.
 

### 2018-09-04 resource_justification.tex
Edited other docs

@@
   \vspace{-3mm}
-  \section{Directly Incurred Costs: 20,819 (all values in GBP)}
+  \section{Directly Incurred Costs: 36,444 (all values in GBP)}
   \vspace{-3mm}
-  {\bf Networking events:} We will hold three 3-day networking events in Chiang-Rai to be attended by all co-I's, students and representatives from the external partners (up to 30 people).
-The first is to introduce the team to the external partners and to start to understand their needs, a second after six months to discuss and finalise broad specifications of what we will deliver, and a third at the end of the project for feedback and to explore future prospects of the partnerships.
-Each event is costed at 2728 and covers: hotel and flight costs for 5 participants not based in Chiang-Rai (1172), transport within Chiang-Rai (234), food and drink (970) and meeting room (352).
-Total: 8184.
-{\bf Transport to partners:} We have budgeted 773 for transport to the external partners' sites during the course of the project.
-{\bf User training:} We will hold a six-day workshop to train the external partners in the use of our systems.
-For this, we have budgeted for: meeting room (703), food and drink (646), transport (609).
-Total: 1959.
-{\bf Consumables:} We request 7500 to buy a network of five high-performance computers.
-This is the minimum needed to produce a working distributed database on which the external partners' data can be stored and managed effectively.
-On this network, we will install the {\it Hadoop} databasing ecosystem - the most widely-used solution for distributed data storage, management and analytics system - and use it to both research the optimum data storage and management solutions for our external partners and to train the end users.
-The network will consist of 1$\times$Hadoop cluster management module (Quad-core, 32 GB RAM; 1406), 1$\times$Database service module (Quad-core, 32 GB RAM; 1406), 1$\times$Hadoop Namenode (Quad-core, 32 GB RAM; 1406), 2$\times$Hadoop Datanodes (Quad core, 64 GB RAM each; total for both 3281).
-{\bf Outreach:} At the end of the project, we will host an outreach event in a public space (e.g., shopping mall) to demonstrate to the public and other businesses (i.e., potential future partners) the benefits of science in general and data science specifically.
-Total: 2403
+  {\bf Networking events:} We will hold four 3-day networking events in Chiang-Rai to be attended by all co-I's, students and representatives from the external partners (up to 30 people).
+The first is to introduce the teams to the external partners and to start to understand their needs, a second after six months to discuss and finalise broad specifications of what we will deliver.
+This will be repeated in year two for the new cohort of students (and any potential new partners).
+Each event is costed at 2851 and covers: hotel and flight costs for participants not based in Chiang-Rai (1986), transport within Chiang-Rai (230), food and drink (634).
+Total: 11404.
+{\bf Transport to partners:} We have budgeted 4468 per year for transport to and accomodation wile at the external partners' sites during the course of the project (8936 total).
+{\bf MOOC and Training:} Based on prior experience, we have budgeted 10,000 (covering outsourced design, filming, editing, and translating, plus web hosting) for the development of the MOOC to provide training beyond MFU students, and 3052 to hold the training workshops for people enrolled on the MOOC.
+For the latter, we have budgeted for: food and drink (1030), transport (919), consumables (1103).
+{\bf Outreach:} During the project, we will host four outreach events in publics to demonstrate to the school-age children the benefits of science in general and data science specifically.
+Total: 3052
 
   \vspace{-3mm}
-  \section{Investigator Effort: 41,250}
+  \section{Investigator Effort: XXXX}
   \vspace{-3mm}
-  {\bf Thai salaries:} There are seven Thai co-Is on the grant, six of which we request 0.2FTE each.
-We request an extra 0.2FTE for Dr.
-Boongoen to account for his managerial role on the project (resulting in 0.4FTE for him).
-The 0.2FTE is justified on the basis that all co-I's will attend the 3-day networking events (plus 1 day each to assist with organising the events) and the six-day workshop (18 days total).
-Each Thai co-I is then required to commit the equivalent of 1 day per fortnight to the project (24 days).
+  {\bf Thai salaries:} There are eleven Thai co-Is on the grant, for which we request 0.2FTE each.
+The 0.2FTE is justified on the basis that all co-I's will attend the 3-day networking events (plus 1 day each to assist with organising the events) and the four-day workshop (20 days total).
+Each Thai co-I is then required to commit the equivalent of 1 day per fortnight to the project (48 days).
 This corresponds to 0.18FTE, which we round to 0.2FTE to cover any extra time spent on the project.
-Total: 23598 {\bf UK FEC:} Following the same justification, we request 0.2FEC for Mullaney (salary, NI, pension, Estates, Indirect costs), of which STFC will cover 80\%.
-Total STFC contribution: 17652
+Total: 46,320 {\bf UK FEC:} Following the same justification, we request 0.2FEC for Mullaney (salary, NI, pension, Estates, Indirect costs), of which STFC will cover 80\%.
+Total STFC contribution: XXXX
 
   \vspace{-3mm}
-  \section{Indirect and Estate costs at Thai Institutions: 4,720}
+  \section{Indirect and Estate costs at Thai Institutions: 9264}
   \vspace{-3mm}
@@
   \vspace{-3mm}
-  \section{Travel and subsistence: 6,568}
+  \section{Travel and subsistence: 11,424}
   \vspace{-3mm}
-  {\bf Thai co-Is/researchers:} We request 1000 per person to cover the costs of return flights from Thailand to the UK for two research students to visit the GOTO collaboration for one week.
-We also request 100 per person per day for hotels and subsistence.
-Total: 3400 {\bf UK PI:} We request 1000 for each return flight for Mullaney to attend each networking event.
+  {\bf Thai co-Is/researchers:} We request 2000 per person to cover the costs of two return flights from Thailand to the UK for two research students to visit the GOTO collaboration for one week.
+We also request 100 per person per day for hotels and subsistence, and 100 per person per year for visas.
+Total: 7200 {\bf UK PI:} We request 1000 for each return flight for Mullaney to attend each networking event.
 Mullaney's accommodation and subsistence during the event are already included in the direct costs.
 Mullaney will stay for a further four nights after each event, for which we request accommodation and subsistence costs of 80 per day.
-Total STFC contribution (at 80\%): 3168.
+Total STFC contribution (at 80\%): 4224.
 
   \vspace{-3mm}
-  \section{Total Request: 73,357}
+  \section{Total Request: XXXX}
 

### 2018-09-05 case_for_support.tex
Polishing Case for Support

@@
 This is most sustainable when using home-grown talent to provide these services.
-As such, providing relevant, high quality training in these digital skills to Thai students and workers is a major element in helping the Thai economy to graduate from middle to upper income.
+As such, providing relevant, high quality training in these digital skills to Thai students and workers is a major element in helping Thailand graduate from a middle to an upper income economy.
 
@@
 To date, this programme has been highly productive, as evidenced by:
-  \begin{itemize}
-    \item two students presenting peer-reviewed proceedings at three international conferences (one of whom was awarded a ``Best Presentation'' prize);
-    \item the publication of five peer-reviewed journal articles or conference proceedings;
-    \item successfull collaborations with five external business at the regional level;
-    \item keen interest from four national businesses to work with us in solving their data handling and analysis needs.
+  \begin{itemize}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
+    \item two students presenting peer-reviewed proceedings at three international conferences (one of whom was awarded an ``Excellent Oral Presentation'' award at the 10th International Conference on Machine Learning and Computing);
+    \item the publication of five peer-reviewed journal articles or conference proceedings, one of which was recently awarded the ``Best Conference Paper'' award at the 2018 IEEE International Conference on Knowledge, Innovation and Invention;
+    \item successfull collaboration with five external business at the regional level;
+    \item keen interest from four additional national businesses to work with us in solving their data handling and analysis needs.
   \end{itemize}
-  By building on these sucesses and expanding our external partnerships to a national level, the next phase of our project will establish Mae Fah Luang University (MFU; the Thai PI institute) as a hub for data science research and training within northern Thailand.
-This will enable future students, businesses and organisations to benefit indefinitely from STFC's investment.
+  By building on these sucesses and expanding our external partnerships to a national level, the next phase of our project -- for which we now request funding -- will establish Mae Fah Luang University (MFU, the Thai PI institute) as a hub for data science research and training within northern Thailand.
+This will enable future students, businesses and organisations within Thailand to benefit indefinitely from STFC's current investment.
 
@@
   \noindent
-  Our collaboration started in February, 2017, with a 12-month Newton-funded project.
-For this project, our team worked with Thai graduate students research and develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO).
+  Our collaboration started in February, 2017, with a 12-month STFC Newton-funded project followed by a further 24-month extension.
+For the Newton project, our team works with Thai graduate students to research and develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO).
 GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}.
-This large, constantly-updated dataset gave the students the opportunity to develop the skills and techniques needed to handle and analyse the kinds of Big Data generated by many of today's industries.
-Following this first phase of the project, we were awarded a further two years' of Newton funding from February 2018 to continue our work with GOTO.
-
-  \vspace{2mm}
-  \noindent
-  The primary {\it research} goals of our Newton project are to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated Machine-Learning (ML) algorithms capable of quickly and robustly categorising sources detected by GOTO.
-Our research has led to some novel solutions.
-For the database component are researching whether distributed non-relational databases are an effective means of storing and analysing large astronomical datasets.
+The primary {\it research} goals of our Newton project are to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated ML algorithms to quickly and robustly categorise sources detected by GOTO.
+For the database component we are researching whether distributed non-relational databases (of the type frequently employed by tech industries) are an effective means of storing and analysing large astronomical datasets.
 For the ML component, we are developing effective new methods to train algorithms to identify and classify very rare transient events among tens of thousands of astronomical sources.
-Since both goals are to address challenges associated with archiving and analysing large amounts of astronomical data, the science, technology and expertise involved in the proposed GCRF project has originated from work associated with STFC's core Science Programme.
+Since both goals are to address challenges associated with archiving and analysing large amounts of astronomical data, the science, technology and expertise developed within our collaboration has originated from work associated with STFC's core Science Programme.
 
@@
   \noindent
-  During the first phase of our Newton-funded project, it became clear that the technologies we are developing and the training we are providing would be of great use to a broad range of organisations and businesses within Thailand.
-With this in mind, we successfully applied to STFC's 2017 call for GCRF Foundation funding to research how we could adapt the technology and training we developed during our Newton project to increase the productivity of Thai businesses and organisations.
-Through this project, our researchers and students have gained experience of working with five such external partners, and have been praised for their achievements so far (see support letter from Thanapiriya).
+  During our Newton-funded project, it became clear that the technologies we are developing and the training we are providing would be of great use to a broad range of organisations and businesses within Thailand.
+With this in mind, we successfully applied for a STFC GCRF Foundation Award to research how we could adapt the technology and training we developed during our Newton project to increase the productivity of Thai businesses and organisations.
+This funding has been used to hold two networking events between our students and five external partners (one in March, 2018, the next in September, 2018), purchase a data server onto which partners' data has been uploaded, and provide training and supervision to five teams of 5-7 students while they collaborate with each of our external partners.
+Despite being only half way through the 12-month project, our students are already being praised by our external partners for their achievements so far (see support letter from Thanapiriya).
 
@@
   \noindent
-  Our GCRF-funded project has demonstrated our ability to successfully collaborate with external organisations.
-Presently, our external partners have a regional, as opposed to national or international, presence.
-While working with these small-to-medium sized businesses and organisations has provided our team with invaluable experience of liasing with external partners, our long-term goal is to also work with partners with a national presence within Thailand.
-Doing so will provide MFU with the exposure needed to become self-sustaining in terms of attracting a variety of future external partners.
+  With our GCRF Foundation Award, we have built the computer infrastructure and demonstrated our teams' ability to work with students to help address the data storage and analysis needs of Thai businesses and organisations.
+During that ``capacity-building'' phase, we focussed on small-to-medium sized partners with a regional presence to ensure we didn't overstretch our teams during that early stage.
+The progress made and lessons learned over the past six months make us confident that we are capable of expanding our network of external partners to a national level, including some large enterprises (see the descriptions of the partners below).
+Doing so will provide MFU with the exposure needed to become self-sustaining in terms of attracting a variety of future external partners and establishing it as a hub for data science research and training within nortern Thailand.
 
@@
   \noindent
-  For this capacity-building project, we request funds to expand upon our GCRF Foundation Award-funded project to work with four further external partners, each of which have a more national presence than the partners involved with the our Foundation project.
+  To support the expansion of our project to a national level, we request funds to host another series of networking events for our students
+
+  expand upon our GCRF Foundation Award-funded project to work with four further external partners, each of which have a more national presence than the partners involved with the our Foundation project.
 We also request funding to continue our successful collaboration with Thanapiriya -- the largest of our first partners.

### 2018-09-05 case_for_support.tex
Edited CfS

@@
     \item the publication of five peer-reviewed journal articles or conference proceedings, one of which was recently awarded the ``Best Conference Paper'' award at the 2018 IEEE International Conference on Knowledge, Innovation and Invention;
-    \item successfull collaboration with five external business at the regional level;
-    \item keen interest from four additional national businesses to work with us in solving their data handling and analysis needs.
+    \item our successfull ongoing collaboration with five external businesses and organisations;
+    \item keen interest from four additional national businesses and organisations to work with us in solving their data handling and analysis needs.
   \end{itemize}
@@
   \noindent
-  Our collaboration started in February, 2017, with a 12-month STFC Newton-funded project followed by a further 24-month extension.
+  Our collaboration started in February, 2017, with a 12-month STFC Newton-funded project followed by a further 24-month Newton grant.
 For the Newton project, our team works with Thai graduate students to research and develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO).
 GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}.
-The primary {\it research} goals of our Newton project are to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated ML algorithms to quickly and robustly categorise sources detected by GOTO.
-For the database component we are researching whether distributed non-relational databases (of the type frequently employed by tech industries) are an effective means of storing and analysing large astronomical datasets.
-For the ML component, we are developing effective new methods to train algorithms to identify and classify very rare transient events among tens of thousands of astronomical sources.
-Since both goals are to address challenges associated with archiving and analysing large amounts of astronomical data, the science, technology and expertise developed within our collaboration has originated from work associated with STFC's core Science Programme.
+The primary {\it research} goals of our Newton project are to: (a) develop a data warehouse that is capable of storing large amounts of data that updated on a daily basis, yet is readily analysed at any time and (b) develop fully-automated ML algorithms to quickly and robustly categorise sources detected by GOTO.
+Our research in this area has been recognised as cutting edge within the field of data science, with two of our students winning awards for their presentations at two major international data science conferences (see attachments).
+With our Newton projects focussing on archiving and analysing large amounts of astronomical data, the science, technology and expertise developed within our collaboration has originated from work associated with STFC's core Science Programme.
 
@@
   \noindent
-  During our Newton-funded project, it became clear that the technologies we are developing and the training we are providing would be of great use to a broad range of organisations and businesses within Thailand.
+  During our Newton-funded project, it became evident to us that the technologies we are developing and the training we are providing would be of great use to a broad range of organisations and businesses within Thailand.
 With this in mind, we successfully applied for a STFC GCRF Foundation Award to research how we could adapt the technology and training we developed during our Newton project to increase the productivity of Thai businesses and organisations.
-This funding has been used to hold two networking events between our students and five external partners (one in March, 2018, the next in September, 2018), purchase a data server onto which partners' data has been uploaded, and provide training and supervision to five teams of 5-7 students while they collaborate with each of our external partners.
-Despite being only half way through the 12-month project, our students are already being praised by our external partners for their achievements so far (see support letter from Thanapiriya).
+This funding has been used to (i) hold two networking events between our students and five external partners (one in March, 2018, the next in September, 2018), (ii) purchase a data server onto which partners' data has been uploaded, and (iii) provide training and supervision to five teams of 5-7 students while they collaborate with each of our external partners.
+Despite being only half way through the 12-month project, our students are already being praised by our external partners for their achievements to date (see letter from Thanapiriya).
 
@@
   \noindent
-  With our GCRF Foundation Award, we have built the computer infrastructure and demonstrated our teams' ability to work with students to help address the data storage and analysis needs of Thai businesses and organisations.
-During that ``capacity-building'' phase, we focussed on small-to-medium sized partners with a regional presence to ensure we didn't overstretch our teams during that early stage.
+  With our GCRF Foundation Award, we have provided training to approximately thirty MFU students, giving them the confidence and skills needed to use our in-house computer infrastructure to address the data-related needs of Thai businesses and organisations.
+During that ``capacity-building'' phase, we focussed on small-to-medium-sized partners with a regional presence to ensure we didn't overstretch our teams during that early stage.
 The progress made and lessons learned over the past six months make us confident that we are capable of expanding our network of external partners to a national level, including some large enterprises (see the descriptions of the partners below).
-Doing so will provide MFU with the exposure needed to become self-sustaining in terms of attracting a variety of future external partners and establishing it as a hub for data science research and training within nortern Thailand.
+Doing so will give MFU the exposure needed to become self-sustaining in terms of attracting a variety of future external partners and establishing it as a hub for data science research and training within nortern Thailand.
 
@@
   \noindent
-  To support the expansion of our project to a national level, we request funds to host another series of networking events for our students
-
-  expand upon our GCRF Foundation Award-funded project to work with four further external partners, each of which have a more national presence than the partners involved with the our Foundation project.
-We also request funding to continue our successful collaboration with Thanapiriya -- the largest of our first partners.
+  To support the expansion of our project to a national level, we request funds to host another series of networking events for a new cohort of students to establish collaborations with a set of new external partners, plus Thanapiriya -- the largest of our first partners.
+We also request funding to support the supervision of these students throughout the collaboration with the external partners.
 All our external partners have already agreed to work with us throughout the 24-month project (see Letters of Support).
-At the end of the first 12 months, however, we will hold a networking event to attract other external partners.
 Below, we provide a brief description of the external partners and their data needs:
@@
   \begin{itemize}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
-    \item {\bf Thai AirAsia} is part of the AirAsia group, which is the largest budget airline operating in South East Asia.
+    \item {\bf Thai AirAsia} is part of the AirAsia group, the largest budget airline operating in South East Asia.
 They are renowned among the air industry for their high levels of aircraft utility.
-A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while they wait for the delivery of spare parts.
+A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while waiting for the delivery of replacement parts.
 This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement.
-AirAsia engineers will share their flight data with the students working on this project so that we can adapt the technologies we have developed to better predict when parts will require replacement.
+AirAsia engineers will share their flight data with the students working on this project, and work with them to adapt our technologies to better predict when parts will require replacement.
     \item {\bf Thanapiriya} is a chain of supermarkets spread across various locations in Northern Thailand.
-They have expanded rapidly over the past decade, and are now looking to expand into more locations.
-A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store.
+The business has grown rapidly over the past decade, and are now looking to expand into more locations.
+A problem they face when opening new stores is how to predict customer demographics, which has knock-on effects on how to stock the new store.
 Their aim is to work with a small group of students and researchers to research effective means to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
     \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand.
-Deevana use promotions help attract guests to their hotels.
-At present they use a scatter-gun approach to advertise these promotions, whereas they would like to investigate whether more targeted campaigns based on customer need can deliver better results.
-Deevana wishes for our students to research how machine learning -- in particular clustering analysis -- could be used to better identify different types of customers and test which promotions are most effective at attracting different customer types.
+Deevana use promotions to attract guests to their hotels.
+At present they use a scatter-gun approach to advertise these promotions, whereas they wish to investigate whether more targeted campaigns based on customer need can deliver better results.
+Deevana will work with our students to research how machine learning -- in particular clustering analysis -- could identify different types of customers and test which promotions are most effective at attracting different customer types.
     \item {\bf Biophics} is a Center of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok.
 They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand.
-Biophics would like to work with our students to develop a ML-based algorithm to identify outliers in Tuberculosis (TB) patient records that may help to identify instances of drug resistance.
+Biophics wishes to work with our students to develop a ML-based algorithm to identify outliers in Tuberculosis (TB) patient records that may help to identify instances of drug resistance.
 This is a ``rare event'' problem similar to the one we have developed solutions to for analysing GOTO data.
@@
 In order to grow, OpenLandscape needs to attract customers, but also be able to predict when those customers will place greatest load on their systems.
-OpenLandscape would like to work with a group of our students to (a) analyse their customer database and usage logs to classify customers according to their usage type, which they will use to target potential customers with bespoke promotions and; (b) analyse the usage logs of their hardware to predict those times when there is heaviest load on their systems.
+OpenLandscape would like to work with our students to (a) analyse their customer database and usage logs to classify customers according to their usage type, and (b) analyse the usage logs of their hardware to predict those times when there is heaviest load on their systems.
   \end{itemize}
-  %Being part of Mahidol University -- Thailand's top-ranked medical school -- Biophics is highly familiar with the anonymisation of patient data to the levels required by Thai law, and no patient data will be shared outside Thailand
+  Following the first twelve months of the project, we will hold another networking event to help attract more external partners to work with a new cohort of students.
+
+  \vspace{2mm}
+  \noindent
+  By working closely with external partners, our team of researchers and trainers are gaining significant insights into the skills shortages experienced by Thai businesses.
+This makes our team extremely well-suited to providing highly relevant training to broader sections of Thai society beyond those that are able to attend university, particularly those already those already in full-time employment.
+To capitalise on this opportunity, we request funding to develop a distance-learning course in data science skills that are in high demand by Thai businesses.
+This will be achieved, in part, through a Massive Open Online Course (MOOC).
+We will consult our partners during the design process to ensure that the MOOC addresses the skills gaps that they have identified within the Thai workforce, while also ensuring that the courses are accessible to current and potential employees.
+On successful completion of the course, participants will have the opportunity to attend one of four workshops that we will hold at MFU during that final 7 months of the project.
+The aim of this workshop will be to enable participants to collaborate with members of our team to apply the technologies they have learned during the MOOC to solve either their own data-related problems, or one of a suite of pre-defined problems using our team's own data.
+
+  \vspace{2mm}
   \noindent
   {\large \bf 1.3 Description of work to be undertaken}
-
-  \noindent
-  {\bf 1.3.1 Working with external partners}
 
@@
   \end{enumerate}
-
-  \vspace{2mm}
-  \noindent
-  {\bf 1.3.2 Development of a Thai data science MOOC}
-
-  \noindent
-  With our partnerships with external organisations and businesses, we are able to provide world-class training in data science to Thai students enrolled at MFU, who can then take these skills to the workplace.
-However, this neglects the tens of thousands of other Thai citizens who could benefit from these skills, not least those already in full-time employment who are unable to take time off to attend University.
-The development in recent years of the Massive Open Online Course (MOOC) enables higher education institutes to greatly increase the impact of their teaching.
-
-  \vspace{2mm}
-  \noindent
-  During the final 18 months of the funded project, our team will draw upon our broader teaching experience to develop a series of data science MOOCs.
-Crucially, we will use our unique collaborations with our external partners when developing these course.
-We will consult our partners during the design process to ensure that the course both meet the skills gaps that they have identified within the Thai workforce, while also ensuring that the courses are accessible to current and potential employees.
-On successful completion of the course, participants will have the opportunity to attend one of four workshops that we will hold at MFU during that final 7 months of the project.
-The aim of this workshop will be to enable participants to collaborate with members of our team to apply the technologies they have learned during the MOOC to solve either their own data-related problems, or one of a suite of pre-defined problems using our team's own data.
 

### 2018-09-06 case_for_support.tex
Added new Gantt Chart

@@
   \noindent
-  Our collaboration started in February, 2017, with a 12-month STFC Newton-funded project followed by a further 24-month Newton grant.
+  Our collaboration started in February, 2017, with a 12-month STFC Newton project followed by a further 24-month Newton grant.
 For the Newton project, our team works with Thai graduate students to research and develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO).
 GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}.
-The primary {\it research} goals of our Newton project are to: (a) develop a data warehouse that is capable of storing large amounts of data that updated on a daily basis, yet is readily analysed at any time and (b) develop fully-automated ML algorithms to quickly and robustly categorise sources detected by GOTO.
-Our research in this area has been recognised as cutting edge within the field of data science, with two of our students winning awards for their presentations at two major international data science conferences (see attachments).
-With our Newton projects focussing on archiving and analysing large amounts of astronomical data, the science, technology and expertise developed within our collaboration has originated from work associated with STFC's core Science Programme.
+The primary {\it research} goals of our Newton project are to: (a) develop a data warehouse that is capable of storing large amounts of data that is updated on a daily basis, yet is readily analysed using complex algorithms and (b) develop fully-automated ML algorithms to quickly and robustly categorise sources detected by GOTO.
+Our research in this area has been recognised as cutting edge within the field of data science, with our students winning awards for their presentations at two major international data science conferences (see attachments).
+With our Newton projects focussing on storing and analysing large amounts of astronomical data, the science, technology and expertise developed within our collaboration has originated from work associated with STFC's core Science Programme.
 
@@
   Following the first twelve months of the project, we will hold another networking event to help attract more external partners to work with a new cohort of students.
+We have also budgetted for two Thai researchers to visit the UK twise during the project to help expand the project to include UK partners.
 
-  \vspace{2mm}
   \noindent
-  By working closely with external partners, our team of researchers and trainers are gaining significant insights into the skills shortages experienced by Thai businesses.
-This makes our team extremely well-suited to providing highly relevant training to broader sections of Thai society beyond those that are able to attend university, particularly those already those already in full-time employment.
-To capitalise on this opportunity, we request funding to develop a distance-learning course in data science skills that are in high demand by Thai businesses.
+  By working closely with external partners, our team of researchers are gaining deep insights into the skills shortages experienced by Thai businesses.
+This makes our team extremely well-suited to providing highly relevant training to broader sections of Thai society beyond those that are able to attend university, including those already in full-time employment.
+To capitalise on this opportunity, we request funding to develop a distance-learning course to teach the data-handling skills that are in high demand by Thai businesses.
 This will be achieved, in part, through a Massive Open Online Course (MOOC).
-We will consult our partners during the design process to ensure that the MOOC addresses the skills gaps that they have identified within the Thai workforce, while also ensuring that the courses are accessible to current and potential employees.
-On successful completion of the course, participants will have the opportunity to attend one of four workshops that we will hold at MFU during that final 7 months of the project.
-The aim of this workshop will be to enable participants to collaborate with members of our team to apply the technologies they have learned during the MOOC to solve either their own data-related problems, or one of a suite of pre-defined problems using our team's own data.
+We will consult our partners during the design process to ensure that the MOOC addresses the skills gaps they face and to ensure that the courses are accessible to current and potential employees.
+On successful completion of the course, participants will have the opportunity to attend one of four workshops that we will hold at MFU during the final seven months of the project.
+The aim of this workshop will be to enable participants to collaborate with members of our team to apply the technologies they have learned during the MOOC to solve either their own data-related problems, or one of a suite of pre-defined problems based on using our team's own data.
 
@@
   \begin{enumerate}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
-  \item Host the first networking event in Chiang-Rai, Thailand (where most of the Thai co-Is are based), attended by all UK and Thai team members and representatives from all our pre-identified external partners.
+  \item Host the first networking event in Chiang-Rai, Thailand (where most of the Thai co-Is are based), attended by all UK and Thai team members, students,and representatives from all our pre-identified external partners.
 At the event, our team will deliver a series of short (5-10 minute) presentations to highlight our data-led solutions developed during the first GCRF-funded project.
@@
   \item Each partner will be assigned a staff researcher as a main contact, who will also lead the supervision of a group of final-year project students.
-The role of the primary contact is to coordinate fortnightly meetings with the external partner to provide progress updates and receive feedback.
-Within the first three months of the project, the students will visit and work with each external user for at least 2 weeks to ensure they fully understand the data and problem.
-  \item Around month 4 each team's will transition to the implementation phase by increasingly focusing on adapting our technology and techniques to the needs of the external partners.
+The role of the primary contact is to coordinate fortnightly discussions with the external partner to provide progress updates and receive feedback.
+Within the first three months of the project, the students will visit and work with each external user for at least two weeks to ensure they fully understand the data and problem.
+  \item Around month four each team will transition to the implementation phase by focusing on adapting our technology and techniques to the needs of the external partners.
 During the fortnightly meetings the teams will demonstrate their solutions and encourage the client to suggest improvements.
-  \item During month 7, we will host another meeting between UK and Thai team members and representatives from all external partners.
+  \item During month seven, we will host another meeting between UK and Thai team members and representatives from all external partners.
 This will allow us to revisit the tasks accomplished in the first half, specify the limitations/difficulties identified during the past six months, and revise the working plan for the rest of the projects.
 Plans will be made for further on-site visits and internships.
+Around this time, we will also start work on developing the MOOC, following consultation with our external partners.
   \item Our work will focus on delivering the agreed systems by adapting our own and further researching new technnologies to meet our partners' needs.
@@
 This event will be attended by other potential partners to work with a new cohort of final-year students during months 13-24.
+  \item The next twelve months of the partner-focussed part of the project will follow a similar schedule as the first twelve months, but with a new cohort of students and new external partners.
+Around month twelve, we will broadcast our MOOC
   \end{enumerate}

### 2018-11-29 case_for_support.tex
First commit in long time

@@
 
-  \vspace{3mm}
+  \vspace{2mm}
   \noindent
@@
 This is most sustainable when using home-grown talent to provide these services.
-As such, providing relevant, high quality training in these digital skills to Thai students and workers is a major element in helping Thailand graduate from a middle to an upper income economy.
+As such, providing relevant, high quality training in these digital skills to Thai students and workers is a major element in helping Thailand graduate from a middle to an upper-income economy.
 
@@
     \item the publication of five peer-reviewed journal articles or conference proceedings, one of which was recently awarded the ``Best Conference Paper'' award at the 2018 IEEE International Conference on Knowledge, Innovation and Invention;
-    \item our successfull ongoing collaboration with five external businesses and organisations;
-    \item keen interest from four additional national businesses and organisations to work with us in solving their data handling and analysis needs.
+    \item our successful ongoing collaboration with five external Thai businesses and organisations;
+    \item keen interest from four additional national businesses and organisations to work with us in solving their data handling and analysis needs (see Letters of Support).
   \end{itemize}
-  By building on these sucesses and expanding our external partnerships to a national level, the next phase of our project -- for which we now request funding -- will establish Mae Fah Luang University (MFU, the Thai PI institute) as a hub for data science research and training within northern Thailand.
+  By building on these successes and expanding our external partnerships to a national level, the next phase of our project -- for which we now request funding -- will establish Mae Fah Luang University (MFU, the Thai PI institute) as a hub for data science research and training within northern Thailand.
 This will enable future students, businesses and organisations within Thailand to benefit indefinitely from STFC's current investment.
@@
 With this in mind, we successfully applied for a STFC GCRF Foundation Award to research how we could adapt the technology and training we developed during our Newton project to increase the productivity of Thai businesses and organisations.
-This funding has been used to (i) hold two networking events between our students and five external partners (one in March, 2018, the next in September, 2018), (ii) purchase a data server onto which partners' data has been uploaded, and (iii) provide training and supervision to five teams of 5-7 students while they collaborate with each of our external partners.
-Despite being only half way through the 12-month project, our students are already being praised by our external partners for their achievements to date (see letter from Thanapiriya).
+This funding has been used to (i) hold two networking events between our students and five external partners (one in March, 2018, the next in September, 2018), (ii) purchase a data server onto which partners' data has been uploaded, and (iii) provide training and supervision to five teams of 5-7 students while they collaborate with each of our external partners to solve their data-related problems.
+Our students are already being praised by our external partners for their achievements to date (see Letter of Support from Thanapiriya).
 
@@
 The progress made and lessons learned over the past six months make us confident that we are capable of expanding our network of external partners to a national level, including some large enterprises (see the descriptions of the partners below).
-Doing so will give MFU the exposure needed to become self-sustaining in terms of attracting a variety of future external partners and establishing it as a hub for data science research and training within nortern Thailand.
+Doing so will give MFU the exposure needed to become self-sustaining in terms of attracting a variety of future external partners and establishing it as a hub for data science research and training within northern Thailand.
 
@@
   \noindent
-  To support the expansion of our project to a national level, we request funds to host another series of networking events for a new cohort of students to establish collaborations with a set of new external partners, plus Thanapiriya -- the largest of our first partners.
+  {\large \bf 1.3 Description of work to be undertaken}
+
+  \noindent
+  To support the expansion of our project to a national level, we request funds to host another series of networking events during which a new cohort of students will initiate collaborations with a new set of external partners, plus Thanapiriya -- the largest of our first partners.
 We also request funding to support the supervision of these students throughout the collaboration with the external partners.
 All our external partners have already agreed to work with us throughout the 24-month project (see Letters of Support).
-Below, we provide a brief description of the external partners and their data needs:
+We provide a brief description of the external partners and their data needs below:
 
@@
 A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while waiting for the delivery of replacement parts.
-This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement.
-AirAsia engineers will share their flight data with the students working on this project, and work with them to adapt our technologies to better predict when parts will require replacement.
+This waiting could be reduced if we could predict when parts were likely to require replacement.
+AirAsia engineers will share their flight data with the students, and work with them to adapt our technologies to better predict when parts will require replacement.
     \item {\bf Thanapiriya} is a chain of supermarkets spread across various locations in Northern Thailand.
@@
 A problem they face when opening new stores is how to predict customer demographics, which has knock-on effects on how to stock the new store.
-Their aim is to work with a small group of students and researchers to research effective means to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
+Their aim is to work with a small group of students and researchers to research effective means to characterise their customers on a branch-by-branch basis and predict appropriate levels of stock.
     \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand.
@@
 Deevana will work with our students to research how machine learning -- in particular clustering analysis -- could identify different types of customers and test which promotions are most effective at attracting different customer types.
-    \item {\bf Biophics} is a Center of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok.
+    \item {\bf Biophics} is a Centre of Excellence for biomedical and health informatics operating out of the Faculty of Tropical Medicine at Mahidol University, Bangkok.
 They specialise in the collection and analysis of data relating to the incidence and spread of infectious diseases within Thailand.
 Biophics wishes to work with our students to develop a ML-based algorithm to identify outliers in Tuberculosis (TB) patient records that may help to identify instances of drug resistance.
-This is a ``rare event'' problem similar to the one we have developed solutions to for analysing GOTO data.
+This is a ``rare event'' problem similar to the one we have developed solutions for analysing GOTO data.
     \item {\bf OpenLandscape} is a provider of cloud computing infrastructure and services in Thailand.
@@
   Following the first twelve months of the project, we will hold another networking event to help attract more external partners to work with a new cohort of students.
-We have also budgetted for two Thai researchers to visit the UK twise during the project to help expand the project to include UK partners.
+We have also budgeted for two Thai researchers to visit the UK twice during the project to help expand the project to include UK partners.
 
+%  \vspace{2mm}
   \noindent
@@
 We will consult our partners during the design process to ensure that the MOOC addresses the skills gaps they face and to ensure that the courses are accessible to current and potential employees.
-On successful completion of the course, participants will have the opportunity to attend one of four workshops that we will hold at MFU during the final seven months of the project.
+On successful completion of the course, participants will have the opportunity to attend one of eight workshops (four aimed at IT professionals, four aimed at school pupils) that we will hold at MFU during the final seven months of the project.
 The aim of this workshop will be to enable participants to collaborate with members of our team to apply the technologies they have learned during the MOOC to solve either their own data-related problems, or one of a suite of pre-defined problems based on using our team's own data.
@@
   \noindent
-  {\large \bf 1.3 Description of work to be undertaken}
-
-  \noindent
   Over the 24-month period of the grant, we will (in broadly chronological order; see Gantt Chart):
   \begin{enumerate}[leftmargin=6mm,itemsep=-3pt,topsep=1pt]
-  \item Host the first networking event in Chiang-Rai, Thailand (where most of the Thai co-Is are based), attended by all UK and Thai team members, students,and representatives from all our pre-identified external partners.
+  \item Host the first networking event in Chiang-Rai, Thailand (where most of the Thai co-Is are based), attended by all UK and Thai team members, students, and representatives from all our pre-identified external partners.
 At the event, our team will deliver a series of short (5-10 minute) presentations to highlight our data-led solutions developed during the first GCRF-funded project.
@@
 Around this time, we will also start work on developing the MOOC, following consultation with our external partners.
-  \item Our work will focus on delivering the agreed systems by adapting our own and further researching new technnologies to meet our partners' needs.
+  \item Our work will focus on delivering the agreed systems by adapting our own and further researching new technologies to meet our partners' needs.
 As this happens, the purpose of the fortnightly meetings will progressively shift toward feedback sessions, during which the primary contact will demonstrate our systems and allow the end user to suggest improvements.
@@
 This event will be attended by other potential partners to work with a new cohort of final-year students during months 13-24.
-  \item The next twelve months of the partner-focussed part of the project will follow a similar schedule as the first twelve months, but with a new cohort of students and new external partners.
-Around month twelve, we will broadcast our MOOC
+  \item The next 12 months of the partner-focussed part of the project will follow a similar schedule as the first 12 months, but with a new cohort of students and new external partners.
+  \item Around 15, we will broadcast the MOOCs, which will be followed up during months 17-24 with the workshops for IT professionals and schools pupils.
   \end{enumerate}
@@
   \noindent
-  {\large \bf 2.1 Management plan}
+  {\large \bf 2. Management plan}
 
@@
   Our management plan for this next phase will build upon the successes of and lessons learned during the first, Foundation Award-funded, phase of the project.
-Following the success of the initial networking event at MFU, we will hold the same again at the start of this second phase.
+Following the success of the initial networking event at MFU, we will hold another networking event at the start of this second phase.
 Prior to the networking event, teams consisting of at least one member of staff and 2-3 final year project students will be assigned to each external partner.
@@
 Unfortunately, we found that this first approach led to some students feeling less engaged with the project than others.
-By contrast, the model of using smaller groups of final-year students we have employed in our Newton-funded project has led to high levels of student engagement, so we will follow that same set-up here.
+By contrast, the model of using smaller groups of final-year students we have employed in our Newton-funded project has led to high levels of student engagement, so we will follow that same approach here.
 
@@
   \noindent
-  {\large \bf 2.2 Track record of applicants}
+  {\large \bf 3. Track record of applicants}
 
   \noindent
-  Our multi-disciplinary team of researchers is made up of astronomers, computer and data scientists, computer hardware specialists, a Lecturer in Business Management and Marketingn, and a Sales and Marketing Consultant (pro bono).
+  Our multi-disciplinary team of researchers is made up of astronomers, computer and data scientists, computer hardware specialists, a Lecturer in Business Management and Marketing, and a Sales and Marketing Consultant (who has agreed to work with us on a pro bono basis).
 The UK PI (Mullaney) is an astronomer with extensive experience of analysing data from large astronomical surveys.
@@
 Iam-on is data scientist with expertise in database design, data mining, and developing ML algorithms for automated data analysis.
-Together with Arwatchananukul, Dr.
+Together with Dr.
+Arwatchananukul, Dr.
 Iam-On will oversee the database design elements of the project as well as contributing her expertise on the automated analysis aspects.
@@
 
+  \pagebreak
+
+  \noindent
+  {\large \bf 4. Justification of resources }
+
+  \vspace{3mm}
+  \noindent
+  {\bf Directly Incurred Costs: 36,444 (all values in GBP)}
+
+  \noindent
+  {\bf Networking events:} We will hold four 3-day networking events in Chiang-Rai to be attended by all co-I's, students and representatives from the external partners (up to 30 people).
+The first is to introduce the teams to the external partners and to start to understand their needs, a second after six months to discuss and finalise broad specifications of what we will deliver.
+This will be repeated in year two for a new cohort of students (and any potential new partners).
+Each event is costed at 2851 and covers: hotel and flight costs for participants not based in Chiang-Rai (1986), transport within Chiang-Rai (230), food and drink (634).
+Total: 11404.
+{\bf Transport to partners:} We have budgeted 4468 per year for transport to and accomodation wile at the external partners' sites during the course of the project (8936 total).
+{\bf MOOC and Training:} Based on prior experience, we have budgeted 10,000 (covering outsourced design, filming, editing, and translating, plus web hosting) for the development of the MOOC to provide training beyond MFU students, and 3052 to hold the training workshops for people enrolled on the MOOC.
+For the latter, we have budgeted for: food and drink (1030), transport (919), consumables (1103).
+{\bf Outreach:} In addition to targetting high school pupils with our MOOC, we will also host four outreach events to during which school-age particpants will gain hands-on experience of handling and analysing large digital datasets.
+Total: 3052
+
+  \vspace{3mm}
+  \noindent
+  {\bf Investigator Effort: 86,638}
+
+  \noindent
+  {\bf Thai salaries:} There are eleven Thai co-Is on the grant, for which we request 0.2FTE each.
+The 0.2FTE is justified on the basis that all co-I's will attend the 3-day networking events (plus 1 day each to assist with organising the events) and the four-day workshop (20 days total).
+Each Thai co-I is then required to commit the equivalent of 1 day per fortnight to the project (48 days).
+This corresponds to 0.18FTE, which we round to 0.2FTE to cover any extra time spent on the project.
+Total: 46,320 {\bf UK FEC:} Following the same justification, we request 0.2FEC for Mullaney (salary, NI, pension, Estates, Indirect costs), of which STFC will cover 80\%.
+Total STFC contribution: 40,318
+
+  \vspace{3mm}
+  \noindent
+  {\bf Indirect and Estate costs at Thai Institutions: 9264}
+
+  \noindent
+  As stipulated in the guide, this is calculated at a rate of 20\% of the total Thai investigator salaries.
+
+  \vspace{3mm}
+  \noindent
+  {\bf Travel and subsistence: 11,424}
+
+  \noindent
+  {\bf Thai co-Is/researchers:} We request 2000 per person to cover the costs of two return flights from Thailand to the UK for two research students to visit the GOTO collaboration for one week to meet potential UK partners.
+We also request 100 per person per day for hotels and subsistence, and 100 per person per year for visas.
+Total: 7200 {\bf UK PI:} We request 1000 for each return flight for Mullaney to attend each networking event.
+Mullaney's accommodation and subsistence during the event are already included in the direct costs.
+Mullaney will stay for a further four nights after each event, for which we request accommodation and subsistence costs of 80 per day.
+Total STFC contribution (at 80\%): 4224.
+
+  \vspace{3mm}
+  \noindent
+  {\bf Total Request: 143,770}
+
   \end{document}

### 2018-11-29 impact_statement.tex
First commit in long time

@@
 In the process we have learned new skills and have researched novel databasing and machine learning techniques to overcome some of the challenges inherent to storing and analysing large, constantly-updated digital datasets.
-Our follow-up GCRF Foundation Award has enabled us to work successfully with a small number of local businesses, during which we have demonstrated our ability to engage students in working with external partners.
-We now request follow-on GCRF funding to fully capitalise on our skills and experiences to ensure that MFU becomes a self-sustaining centre for data analytics within Thailand.
+Our follow-up GCRF Foundation Award has enabled us establish successful collaborations with a small number of local businesses, during which we have demonstrated our ability to engage students in working with external partners.
+We now request follow-on GCRF funding to fully capitalise on our skills and experiences to ensure that MFU becomes a self-sustaining centre for research and training in data science within Thailand.
 
@@
   \noindent
-  As well as our overall strategy, we have also placed maximising impact at the forefront of each individual element of the workplan.
-The networking event at the start of the project will enable our team to showcase our data handling/analysis skills and techniques, using GOTO as an example, while also enabling the external partners to describe the data and analysis needs and their desired outcome of the research.
-This will ensure that the whole team is aware of the needs of the external partners from the outset, not just the primary contact, thereby facilitating greater collaboration within the team leading to greater impact.
+  As well as our overall strategy, we have also placed maximising impact at the forefront of each individual element of the work plan.
+The networking event at the start of the project enables our team to showcase our data handling/analysis skills and techniques, using GOTO as an example, while also enabling the external partners to describe the data and analysis needs and their desired outcome of the research.
+This ensures that the whole team is aware of the needs of the external partners from the outset, not just the primary contact, thereby facilitating greater collaboration within the team leading to greater impact.
 
@@
   Maximising impact is also a major consideration in planning how we will work with the external partners throughout the period of the grant.
-From the team's own experience from collaborating on our Newton and prior GCRF projects, regular meetings are by the far the most effective means of making progress when designing data handling and analysis systems to meet a client's needs.
+From the team's own experience from collaborating on our Newton and GCRF Foundation Award projects, regular meetings are by the far the most effective means of making progress when designing data handling and analysis systems to meet a client's needs.
 This is because the client has a better sense of what data fields are more important and/or informative than others, and this must be effectively communicated to the data scientists in order for them to design an effective database or analysis system.
 Usually, however, this is an iterative process that evolves over multiple meetings, which is why we have planned for fortnightly meetings throughout most of the period of the project.
-This also has the benefit of maximising team member's exposure to working with external partners -- valuable experience for building collaborations with larger numbers of businesses and organisations after this initial GCRF grant.
+This also has the benefit of maximising team members' exposure to working with external partners -- valuable experience for building collaborations with larger numbers of businesses and organisations after this initial GCRF grant.
 Finally, we want to make sure that the data solutions we provide to our external partners are effective, which is why we will deliver versions of our systems at the start of month ten for Beta testing.

### 2018-11-29 oda_statement.tex
First commit in long time

@@
   \setcounter{figure}{0}
-  \noindent
-  {\LARGE \bf From Stars to Baht: Broadening the economic impact of \\
-  astronomical data handling techniques in Thailand}
 
-  \vspace{3mm}
   \noindent
   {\LARGE \bf ODA statement}
+
+  \vspace{2mm}
+  \noindent
+  {\bf Fifty word compliance statement:} We will work with Thai businesses and organisations to increase their productivity by providing research and training in high-technology skills.
+This will help to address a skills gap which has been identified as a major barrier to Thailand progressing to an upper-income economy.
 
@@
   \noindent
-  Our team's long-term ambition is to provide Northern Thailand's businesses and organisations with home-grown talent in handling and analysing large quantities of digital data.
-Northern Thailand is one of the regions that have experienced weaker economic growth compared to the rest of the country (World Bank, 2017).
-However, as our Letters of Support demonstrate, businesses and organisations in that area are crying out for access to the data handling and analysis skills and technologies that our team can provide.
-If this demand is not met locally, there is the risk that they and others like them will seek these skills further afield in Bangkok or, worse, from companies not based in Thailand, to the detriment of the local economy.
+  Our team's long-term ambition is to provide Thailand's businesses and organisations with home-grown talent in handling and analysing large quantities of digital data.
+Ultimately, we wish to establish Mae Fah Luang University -- the Thai PI institute -- as a self-sustaining hub for data science research and innovation within Northern Thailand, which is a region that has experienced some of the weakest economic growth compared to the rest of the country (World Bank, 2017).
+As our Letters of Support demonstrate, businesses and organisations across Thailand are crying-out for access to the data handling and analysis skills and technologies that our team have demonstrated we can provide during our GCRF Foundation Award.
+If this demand is not met locally, there is the risk that they and others like them will seek these skills from companies not based in Thailand, to the detriment of the local economy.
 
@@
 We now request funding to support work with a larger, more diverse range of businesses and organisations.
-This will give our team the experience necessary to reach our ultimate goal: to set up a self-sustaining ``Centre of Excellence'' for researching technologies to meet the data handling and analysis needs of businesses and organisations in Northern Thailand.
+This will give our team the experience necessary to reach our ultimate goal: to set up a self-sustaining ``Centre of Excellence'' for researching technologies to meet the data handling and analysis needs of businesses and organisations across Thailand.
 

### 2018-11-29 response.tex

\documentclass[11pt]{article}
\usepackage[a4paper,bindingoffset=0cm,%
            left=2cm,right=2cm,top=2cm,bottom=2cm,%
            footskip=0.5cm]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{multicol}

%\usepackage{psfig}

\usepackage{siunitx,amsmath,amssymb}

\usepackage{sectsty}
\sectionfont{\fontsize{12}{15}\selectfont}
\subsectionfont{\fontsize{11}{15}\selectfont}

%\renewcommand*\sfdefault{phv}
%\renewcommand{\familydefault}{\sfdefault}
\makeatletter
\newenvironment{tablehere}
  {\def\@captype{table}}
  {}

\newenvironment{figurehere}
  {\def\@captype{figure}}
  {}
\makeatother

\begin{document}
%\title{Broadening the impact of astronomical data handling\vspace{-2ex}}
%\maketitle
\setcounter{figure}{0}
\noindent
{\large \bf From Stars to Baht: Phase II}

\noindent
{\large \bf Response to reviewers' reports}

\vspace{2mm}
\noindent
We thank all the reviewers for their constructive feedback on our project, and the panel for giving us the opportunity to respond to their feedback. In what follows, we refer to reviewers 022396196, 057124662 and 039760429 as 02, 03 and 05, respectively.

\vspace{2mm}
\noindent
It is clear that the greatest concern of reviewers 02 and 05 is the apparent lack of support on the UK-side. To address this specific concern, since the submission of the funding application we have garnered offers of support from a significant numbers of UK-based academics and support staff, all of whom possess skills highly relevant to the project. Each have agreed to act as consultants on the project, offering advice where necessary throughout the two-year period. Our consultants include members of the University of Sheffield based in the following Departments/Schools/Teams:
\begin{table}[h]
\begin{tabular}{lll}
  Name & Department/School/Team & Relevant expertise\\
  \hline
  Dr. Mauricio Alvarez Lopez & Computer Science & Machine learning \\
  Prof. Eleni Vasilaki & Computer Science & Machine learning\\
  Mr. David Holloway & Digital Learning Team & MOOC production \\
  Dr. Erica Ballantyne & Management & Operations and supply chain \\
  Dr . Miguel Juarez & Maths \& Statistics & Bayesian methods in Big Data analysis \\
  Prof. Richard Wilkinson & Maths \& Statistics & Statistical analysis of complex systems\\
  Prof. Simon Goodwin & Physics and Astronomy & Big Data analytics \\
  Dr. Richard Parker & Physics and Astronomy & Big Data analytics \\
\hline
\end{tabular}  
\end{table}

\noindent
The members of Computer Science in the above table are also part of Sheffield's Machine Learning Research Network, whose role is to support researchers and students in using and developing Machine Learning. Further, Prof. Simon Goodwin and Dr. Richard Parker have recently been collaborating with Dr. Erica Parker on research projects focussed on the optimisation of transport networks; experience that is particularly relevant to the Air Asia and Thanapirya sub-projects. Mr. David Holloway is a member of Sheffield's in-house, centrally-funded MOOC-production team, and has agreed to offer his advice on developing our MOOC. We do not require any additional funds for our consultants.

\vspace{2mm}
\noindent
The role of our consultants will be to offer advice and guidance to the students and their supervisors during the course of the project. As noted in our Gantt Chart, the core team members will write a detailed progress report every 6 months. This will be disseminated among all our consultants, giving them the opportunity to offer suggestions to the students (e.g., "this sounds like an X problem, you may want to try Y", "you may wish to read this paper..."). As such, the project will remain exactly as stipulated in our application, but with additional support and advice from leading UK experts.

\vspace{2mm}
\noindent
In response to the question of the scalability of the project raised by reviewer 03, we'd like to inform the panel that, since the submission of the application, our team has held a networking event at MFU attended by representatives from {\it all} the proposed external partners highlighted in our application. Most of these representatives travelled from Bangkok ($\sim$1.5hr flight), or even further afield, thereby demonstrating their enthusiasm to be involved in the project. In addition, the goal of developing a MOOC is to enable the project to have a truly national impact. After developing the MOOC in consultation with our proposed external partners and UK experts, we will advertise the free resource to employees of other businesses and organisations within Thailand. On completion of the MOOC, these employees can attend one of our residential workshops to gain further training. This will also raise awareness of the Masters programme at MFU, which will continue to work with additional external partners on new projects beyond the end of the GCRF funding.

\vspace{2mm}
\noindent
Finally, in answer to reviewer 05's question about who and how the MOOC will be developed. This will be done by the core team members with outsourced design \& filming, and in consultation with Sheffield's MOOC production unit (see table). To date, this unit has produced 16 MOOCs, and have agreed to share with our team their knowledge and experience of how to develop a successful MOOC.

\end{document}

### 2018-11-29 response.tex
Added case study to report and made some final minor adjustments

@@
   Dr. Erica Ballantyne & Management & Operations and supply chain \\
-  Dr . Miguel Juarez & Maths \& Statistics & Bayesian methods in Big Data analysis \\
+  Dr. Miguel Juarez & Maths \& Statistics & Bayesian methods in Big Data analysis \\
+  Dr. Kevin Walters &  Maths \& Statistics & Bayesian methods in Big Data analysis \\
   Prof. Richard Wilkinson & Maths \& Statistics & Statistical analysis of complex systems\\
@@
 Richard Parker have recently been collaborating with Dr.
-Erica Parker on research projects focussed on the optimisation of transport networks; experience that is particularly relevant to the Air Asia and Thanapirya sub-projects.
+Erica Ballantyne on research projects focussed on the optimisation of transport networks; experience that is particularly relevant to the Air Asia and Thanapirya sub-projects.
 Mr.
@@
 This will be disseminated among all our consultants, giving them the opportunity to offer suggestions to the students (e.g., "this sounds like an X problem, you may want to try Y", "you may wish to read this paper...").
-As such, the project will remain exactly as stipulated in our application, but with additional support and advice from leading UK experts.
+As such, the project will remain exactly as stipulated in our application, with support and advice from more leading UK experts.
 
@@
 \noindent
-Finally, in answer to reviewer 05's question about who and how the MOOC will be developed.
+In answer to reviewer 05's question about who and how the MOOC will be developed.
 This will be done by the core team members with outsourced design \& filming, and in consultation with Sheffield's MOOC production unit (see table).
@@
 
+\vspace{2mm}
+\noindent
+Finally, reviewer 03 raises the prospect of a case study.
+We expect to convert our work with our current partner, Thanapirya, into a case study.
+Our team of five students have delivered to Thanapirya's Management Team their initial model that predicts their best-selling products given the demographics of the local area.
+Thanapirya have provided feedback and the students are now working toward a mid-December delivery of a live, online system that can be used to help choose future trading locations.
+Once the students have received their final feedback, we will include Thanapirya as a case study in our final report for the 2017 GCRF project (due March, 2019).
+
 \end{document}
